---
title: "stats & figs for gaze as confidence (RSPB revision 03/26)"
author: "Yoni"
date: "`r Sys.Date()`"
output: html_document
---


This is a script for the RSBP revison (March 26)
Script is organized according to Figures in MS. 

```{r load libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(Rmisc)
library(ggpubr)
library(knitr)
library(broom)
library(zoo)
library(lubridate)
library(rstatix)
library(psycho)
library(bayestestR)
library(BayesFactor)
library(pscl)
library(PerformanceAnalytics)
library(lme4)
library(Hmisc)
library(hms)
library(emmeans)
library(vroom)
library (cowplot)
library(ggforce)
library(tidyverse)
```


```{r load functions & parameters}
#parameter file
source(file.path("functions","parameters_4_fig_and_stats_for_publication.R"))

#function file
source(file.path("functions","functions_4_figs_and_stats_for_pub.R"))
```

```{r load data csv}

# load all subject
fname_mean_gz_all_sub<-file.path(path_processed_csv,"all_exp_mean_gz_tbt_all_sub_290824.csv")

mean_gz_all_sub_csv<-read_csv(fname_mean_gz_all_sub,show_col_types = FALSE)

#Pre-registered subject
fname_mean_gz_prereg<-file.path(path_processed_csv,"all_exp_mean_gz_tbt_only_prereg_ss_trials_290824.csv")



mean_gz_prereg_csv<-read_csv(fname_mean_gz_prereg,show_col_types = FALSE)

#slim trkr pre-regesteried (contains only mean gaze direction)
fname_slim_trkr_prereg<-file.path(path_processed_csv,"all_exp_slim_trkr_only_prereg_ss_trials_290824.csv")

slim_trkr_prereg_csv<-vroom(fname_slim_trkr_prereg,show_col_types = FALSE)


#model fitting outputs- using 24/01/24 output (this has all subjects)
# # model parameters
# fname_learn_model_param<-file.path(path_processed_csv,"all_exp_n_sub_param_tbl_120224.csv")
# 
# learn_model_param_all_csv<-read_csv(fname_learn_model_param,show_col_types = FALSE)

# #tbt traj of RW model
# fname_RW_traj<-file.path(path_processed_csv,"all_exp_n_sub_RW_RWS_traj_tbl_150224.csv")
# 
# RW_traj_all_csv<-read_csv(fname_RW_traj,show_col_types = FALSE)


# files for parameter & model recovery
fname_param_recov_csv<-file.path(path_processed_csv,"parameter_model_recovery_files","parameter_recovery_120824.csv")
param_recov_csv<-read_csv(fname_param_recov_csv,show_col_types = FALSE)

```


## prep data

```{r prepping mean_gz_prereg_csv}

#adding ocular "confidence rating"
mean_gz_prereg_csv<-mean_gz_prereg_csv%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(
    mx_gz=max(m_pred_gz),mn_gz=min(m_pred_gz)
  )%>%
  dplyr::rowwise()%>%
  mutate(gz_conf=findInterval(m_pred_gz, seq(mn_gz,mx_gz,length.out=6),all.inside = TRUE))%>% #this bins the condience rating into five equidistant bins
  mutate(gz_conf=gz_conf-3)%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(z_gz_conf=scale_this(gz_conf))%>%
  dplyr::select(-c(mx_gz,mn_gz))%>%
  dplyr::relocate(c(gz_conf,z_gz_conf),.after = m_pred_gz)

```


```{r prep data to correlate explicit and gaze confidence ratings}
#create a df with only experiment 3
mean_gz_prereg_exp3<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name=="Exp. 3")

#zscore explicit confidence ratings
##CENTERING confidence ratings (so the initial point & mid rating is 0)
mean_gz_prereg_exp3<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(orig_conf_rating=conf_rating,
                conf_rating=conf_rating-3)%>% 
  dplyr::relocate(c(orig_conf_rating),.after = conf_rating)

#adding z-score of confidence
mean_gz_prereg_exp3<-mean_gz_prereg_exp3%>%
  group_by(sub_name)%>%
  dplyr::mutate(z_conf_rating=scale_this(conf_rating))%>%
  dplyr::relocate(z_conf_rating,.after=conf_rating)

# getting "eye_confidence rating"
mean_gz_prereg_exp3<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(
    mx_gz=max(m_pred_gz),mn_gz=min(m_pred_gz)
  )%>%
  dplyr::rowwise()%>%
  mutate(gz_conf=findInterval(m_pred_gz, seq(mn_gz,mx_gz,length.out=6),all.inside = TRUE))%>% #this bins the condience rating into five equidistant bins
  mutate(gz_conf=gz_conf-3)%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(z_gz_conf=scale_this(gz_conf))%>%
  dplyr::select(-c(mx_gz,mn_gz))%>%
  dplyr::relocate(c(m_pred_gz ,gz_conf,z_gz_conf),.after = z_conf_rating)


```



# {.tabset .tabset-pills}



## Fig 1& S1&2

### Try Fig1B: overall acc exp 1. 
```{r prep data for  acc per exp all subject}

sum_acc_all_sub<-mean_gz_all_sub_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(acc=mean(is_acc)*100,
                   rule_acc=mean(resp_rule_acc)*100)

# getting only exp 1 &2
sum_acc_all_sub_exp12<-sum_acc_all_sub%>%
  dplyr::filter(exp_name!="Exp. 3")


```


<!-- ```{r viz fig S1 acc per exp all subject} -->
<!-- (plot_fig_1B<- -->
<!--    ggplot(data = sum_acc_all_sub_exp12, -->
<!--           aes(y=acc, x=1))+ -->
<!--    geom_violin(alpha=.4,trim=FALSE)+ -->
<!--    geom_boxplot(alpha=.4,width=.05,outlier.shape = NA)+ -->
<!--    geom_point(position = position_jitter(width=.1),alpha=.8,color="darkgrey")+ -->
<!--    geom_point(shape=3,aes(y=mean(acc)),size=5, color="darkblue")+ -->
<!--    # ylab("% Accuracy")+ -->
<!--      scale_y_continuous(name = "% Accuracy",breaks=c(seq(40,90,by=10)),labels = c("40","50","60","70","80",""),limit=c(40,85))+ -->
<!--      xlab("")+ -->
<!--    geom_hline(yintercept = 50, color="brown1",linetype="dashed")+ -->

<!--    geom_hline(yintercept = 0.55*100, color="orange",linetype=2)+ -->
<!--    theme_classic()+ -->
<!--    theme( -->
<!--      axis.title.y = element_text(size = 14,face="bold"), -->
<!--      axis.text.y = element_text(size = 14,angle=0), -->
<!--      axis.text.x = element_blank(), -->
<!--      axis.title.x = element_blank(), -->
<!--      strip.text = element_text(size = 16,face="bold") -->

<!--    ) -->

<!-- ) -->

<!-- # ggsave(plot = plot_fig_1B,filename = file.path("pics_for_gaze_conf","SM_fig_1B_acc_exp12_v2.jpg"), width=7, height=6.5, units = "cm") -->
<!-- ``` -->
Plotting rule accuracy instead
```{r viz fig 1B rule  acc per exp all subject}
(plot_fig_1B_rule_acc<-
   ggplot(data = sum_acc_all_sub_exp12,
          aes(y=rule_acc, x=1))+
   geom_violin(alpha=.4,trim=TRUE)+
   geom_boxplot(alpha=.4,width=.05,outlier.shape = NA)+
   geom_point(position = position_jitter(width=.1),alpha=.8,color="darkgrey")+
   geom_point(shape=3,aes(y=mean(rule_acc)),size=5, color="darkblue")+
  scale_y_continuous(name = "% Accuracy",breaks=c(seq(40,90,by=10)),labels = c("40","50","60","70","80","90"),limit=c(40,90))+
     xlab("")+
   geom_hline(yintercept = 50, color="brown1",linetype="dashed")+
 
   # geom_hline(yintercept = 0.55*100, color="orange",linetype=2)+
   theme_classic()+
   theme(
     axis.title.y = element_text(size = 14,face="bold"),
     axis.text.y = element_text(size = 14,angle=0),
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     axis.title.x = element_blank(),
     strip.text = element_text(size = 16,face="bold")
     
   )
 
)

# ggsave(plot = plot_fig_1B_rule_acc,filename = file.path("pics_for_gaze_conf","SM_fig_1B_acc_exp12_rule_acc.jpg"), width=10, height=6.5, units = "cm")
```
```{r getting stats of rule acccuracy in exp 1 2}


smry_stats_rule_acc_exp1_2<-sum_acc_all_sub%>%
  dplyr::filter(exp_name!="Exp. 3")%>%
  dplyr::ungroup()%>%
  dplyr::summarise(mean=CI(rule_acc)[2],lo_ci=CI(rule_acc)[3],hi_ci=CI(rule_acc)[1],
                   t=t.test(rule_acc,mu=50)$statistic,df=t.test(rule_acc,mu=50)$parameter, p.val=t.test(rule_acc,mu=50)$p.value, ES=one_sample_ttest_cohen_d(rule_acc))


smry_stats_rule_acc_all_exp<-sum_acc_all_sub%>%
  dplyr::ungroup()%>%
  dplyr::summarise(mean=CI(rule_acc)[2],lo_ci=CI(rule_acc)[3],hi_ci=CI(rule_acc)[1],
                   t=t.test(rule_acc,mu=50)$statistic,df=t.test(rule_acc,mu=50)$parameter, p.val=t.test(rule_acc,mu=50)$p.value)


sum_acc_all_sub %>%
  dplyr::ungroup() %>%
   cohens_d(rule_acc~1,mu = 50) 

knitr::kable(smry_stats_rule_acc_all_exp,digits=3, caption = "rule acc across experiments")
 
```



### Fig 1C : learning curve across subjects

```{r prep data for learning curve of acc all sub}

#subject by subject relative accuracy-per relative trial number
learning_curve_acc_all_sbs<-mean_gz_all_sub_csv%>%
  dplyr::group_by(exp_name,sub_name,rel_trial_number)%>%
  dplyr::mutate(bin_ind=findInterval(rel_trial_number,seq(1,36,by=4)))%>%
  dplyr::group_by(exp_name,sub_name,bin_ind)%>%
  dplyr::summarize(rel_acc_actual=mean(is_acc)*100,
                   rel_acc_rule=mean(resp_rule_acc)*100)

#all subjects
#pivoting to long and adding a column of acc type
learning_curve_acc_all_sbs<-learning_curve_acc_all_sbs%>%
  pivot_longer(!c(exp_name,sub_name,bin_ind), names_prefix = "rel_acc_",names_to="type_acc", values_to = "acc_val")


#group statistic-per relative trial number
learning_curve_acc_grp_all_subs<-learning_curve_acc_all_sbs%>%
  dplyr::group_by(exp_name,bin_ind,type_acc)%>%
  dplyr::summarize(lo_ci=CI(acc_val)[3],hi_ci=CI(acc_val)[1],mean_acc=CI(acc_val)[2])

learning_curve_acc_grp_all_subs_exp12<-learning_curve_acc_all_sbs%>%
  dplyr::filter(bin_ind<9)%>%
  dplyr::filter(exp_name!="Exp. 3")%>%
  # dplyr::filter(type_acc=="rule")%>%
  dplyr::group_by(bin_ind,type_acc)%>%
  dplyr::summarize(lo_ci=CI(acc_val)[3],hi_ci=CI(acc_val)[1],mean_acc=CI(acc_val)[2])

learning_curve_rule_acc_grp_all_subs_exp12<-learning_curve_acc_all_sbs%>%
  dplyr::filter(bin_ind<9)%>%
  dplyr::filter(exp_name!="Exp. 3")%>%
  dplyr::filter(type_acc=="rule")%>%
  dplyr::group_by(bin_ind,type_acc)%>%
  dplyr::summarize(lo_ci=CI(acc_val)[3],hi_ci=CI(acc_val)[1],mean_acc=CI(acc_val)[2])
```

```{r viz learning curve of rule acc all sub exp 12}

#Plot All subjects
#plot learning within block binned by 4 trial 
(plot_fig_1D<-
   ggplot(data=learning_curve_rule_acc_grp_all_subs_exp12,aes(x=bin_ind,y=mean_acc, group=type_acc))+
   geom_line()+
   geom_point()+
   geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci),alpha=.3, color=NA)+
   # geom_line(data=sbs_rel_trial_acc_bin,aes(x=bin_ind,y=rel_actual_acc,group=sub_name),alpha=.2)+
   scale_x_continuous(name=" Trial # (in block)", labels = c("1-4","5-8","9-12","13-16","17-20","21-24","25-28","29-32"),breaks = c(1:8),limit=c(1,8))+
 scale_y_continuous(name = "",breaks=c(seq(40,90,by=10)),labels = c("40","50","60","70","80","90"),limit=c(40,90))+
   geom_hline(yintercept = 50, color="brown1",linetype="dashed")+
   theme_classic()+
   theme(axis.title.x = element_text(size = 14,face="bold"),
         axis.title.y = element_text(size = 14,face="bold"),
         axis.text.x = element_text(size = 12,angle=25),
         axis.text.y = element_text(size = 14,angle=0),
         strip.text = element_text(size = 16,face="bold"),
         legend.position = "none"
         )
)

# ggsave(plot = plot_fig_1D,filename = file.path("pics_for_gaze_conf","fig_1D_learning_curve_exp12_rule_acc.jpg"), width=10, height=7.5, units = "cm")

```

### SM Fig S1 & Table S1& S2
### S1A: overall acc

```{r viz fig S1 acc per exp all subject}
(plot_SM_fig_S1A<-
   ggplot(data = sum_acc_all_sub,
          aes(y=acc, x=1))+
   geom_violin(alpha=.4,trim=FALSE)+
   geom_boxplot(alpha=.4,width=.05,outlier.shape = NA)+
   geom_point(position = position_jitter(width=.1),alpha=.8,color="darkgrey")+
   geom_point(shape=4,aes(y=mean(acc)),size=5, color="red")+
   ylab("% Accuracy")+
   geom_hline(yintercept = 0.5*100, color="red",linetype=1)+
   geom_hline(yintercept = 0.55*100, color="orange",linetype=2)+
   theme_classic()+
   theme(
     axis.title.y = element_text(size = 14,face="bold"),
     axis.text.y = element_text(size = 14,angle=0),
     axis.text.x = element_blank(),
     axis.title.x = element_blank(),
     strip.text = element_text(size = 16,face="bold")
     
   )+
   facet_wrap(~exp_name)
 
)

# ggsave(plot = plot_SM_fig_S1A,filename = file.path(path_export_sm_pics,"SM_fig_S1A.jpg"), width=15, units = "cm")
```

```{r print summary stats of acc Table S1}
#for each experiment seperately
smry_stats_acc_all_sub<-sum_acc_all_sub%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarise(mean=CI(acc)[2],lo_ci=CI(acc)[3],hi_ci=CI(acc)[1],
                   t=t.test(acc,mu=50)$statistic,df=t.test(acc,mu=50)$parameter, p.val=t.test(acc,mu=50)$p.value, ES=one_sample_ttest_cohen_d(acc))

# combined across experiments
smry_stats_acc_comb<-sum_acc_all_sub%>%
  dplyr::ungroup()%>%
  dplyr::summarise(exp_name="combined",mean=CI(acc)[2],lo_ci=CI(acc)[3],hi_ci=CI(acc)[1],
                   t=t.test(acc,mu=50)$statistic,df=t.test(acc,mu=50)$parameter, p.val=t.test(acc,mu=50)$p.value,ES=one_sample_ttest_cohen_d(acc))

#joining
smry_stats_acc_all_sub_comb<-bind_rows(smry_stats_acc_all_sub,
                                       smry_stats_acc_comb)

knitr::kable(smry_stats_acc_all_sub_comb,digits=1,caption = "Table S1: Acc per experiment across all subjects")

```

```{r print summary stats of rule acc Table S1}
#for each experiment seperately
smry_stats_rule_acc_all_sub<-sum_acc_all_sub%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarise(mean=CI(rule_acc)[2],lo_ci=CI(rule_acc)[3],hi_ci=CI(rule_acc)[1],
                   t=t.test(rule_acc,mu=50)$statistic,df=t.test(rule_acc,mu=50)$parameter, p.val=t.test(rule_acc,mu=50)$p.value, ES=one_sample_ttest_cohen_d(rule_acc))

# combined across experiments
smry_stats_resp_rule_acc_comb<-sum_acc_all_sub%>%
  dplyr::ungroup()%>%
  dplyr::summarise(exp_name="combined",mean=CI(rule_acc)[2],lo_ci=CI(rule_acc)[3],hi_ci=CI(rule_acc)[1],
                   t=t.test(rule_acc,mu=50)$statistic,df=t.test(rule_acc,mu=50)$parameter, p.val=t.test(rule_acc,mu=50)$p.value,ES=one_sample_ttest_cohen_d(rule_acc))

#joining
smry_stats_acc_all_sub_comb<-bind_rows(smry_stats_rule_acc_all_sub,
                                       smry_stats_resp_rule_acc_comb)

knitr::kable(smry_stats_acc_all_sub_comb,digits=1,caption = "Table S1: Rule Acc per experiment across all subjects")

```



### SM Fig 1B. Behav benchmarks of learning- acc on Cue valid>invalid

``` {r compare acc on  Cue Valid (CV) vs. Cue Invalid (CIV)}
#prep data
sum_acc_cong_vs_incong<-mean_gz_all_sub_csv%>%
  dplyr::group_by(exp_name,sub_name,is_cue_valid)%>%
  dplyr::summarize(acc=mean(is_acc)*100)

#plot acc on cong vs. incong
(plot_SM_fig_S1B<-
    ggpaired(data =sum_acc_cong_vs_incong,
             x="is_cue_valid", y="acc", id="sub_name",fill = "is_cue_valid",line.color = "lightgrey",line.size = .2 )+
    scale_x_discrete(name= "Trial's Cue Validity")+
    scale_fill_manual(values =c("deeppink1","aquamarine3"),labels=c("Invalid","Valid"))+
    scale_y_continuous(name= "% Accuracy")+
    geom_hline(yintercept = 50, color="red",linetype="dashed")+
    # ggtitle("acc by cue validity (all sub)")+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          legend.position = "none") +
    facet_wrap(~exp_name)
  
)

# ggsave(plot = plot_SM_fig_S1B,filename = file.path(path_export_sm_pics,"SM_fig_S1B.jpg"), width=15, units = "cm")
```

```{r combine plots S1}
#Combining plots
(
  plot_SM_fig_S1_comb<-plot_grid(plot_SM_fig_S1A,plot_SM_fig_S1B, nrow=2,align="v") 
)

# ggsave(plot = plot_SM_fig_S1_comb,filename = file.path(path_export_sm_pics,"SM_fig_S1_comb.jpg"))

```

#### Table S2

```{r print Table S2 summary stats of CV vs CI acc}
#for each experiment seperately
smry_stats_cong_vs_incong<-sum_acc_cong_vs_incong%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(diff_acc=acc-first(acc))%>%
  dplyr::filter(diff_acc!=0)%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarise(mean_diff=CI(diff_acc)[2],lo_ci=CI(diff_acc)[3],hi_ci=CI(diff_acc)[1],
                   t=t.test(diff_acc,mu=0)$statistic,df=t.test(diff_acc,mu=0)$parameter, p.val=t.test(diff_acc,mu=0)$p.value, ES=one_sample_ttest_cohen_d(diff_acc))

# combined across experiments
smry_stats_cong_vs_incong_comb<-sum_acc_cong_vs_incong%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(diff_acc=acc-first(acc))%>%
  dplyr::filter(diff_acc!=0)%>%
  dplyr::ungroup()%>%
  dplyr::summarise(exp_name="combined",mean_diff=CI(diff_acc)[2],lo_ci=CI(diff_acc)[3],hi_ci=CI(diff_acc)[1],
                   t=t.test(diff_acc,mu=0)$statistic,df=t.test(diff_acc,mu=0)$parameter, p.val=t.test(diff_acc,mu=0)$p.value, ES=one_sample_ttest_cohen_d(diff_acc))

#joining
smry_stats_cong_vs_incong_all_sub_comb<-bind_rows(smry_stats_cong_vs_incong,
                                                  smry_stats_cong_vs_incong_comb)

knitr::kable(smry_stats_cong_vs_incong_all_sub_comb,
             digits=1,caption = "Table S2 Diff Acc Cue valid vs Cue Invalid per experiment across all subjects")

```



### SM Figure S2 


#### S2(Left): learning curve of acc- all Subjects


Note! This is graph with all of the subjects
```{r viz learning curve of acc all sub}

#Plot All subjects
#plot learning within block binned by 4 trial 
(plot_SM_fig_S2_right<-
   ggplot(data=learning_curve_acc_grp_all_subs%>%dplyr::filter(bin_ind<9),aes(x=bin_ind,y=mean_acc, group=type_acc,color=type_acc, fill=type_acc))+
   geom_line()+
   geom_point()+
   geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci),alpha=.3, color=NA)+
   # geom_line(data=sbs_rel_trial_acc_bin,aes(x=bin_ind,y=rel_actual_acc,group=sub_name),alpha=.2)+
   scale_x_continuous(name=" Trial # (in block)", labels = c("1-4","5-8","9-12","13-16","17-20","21-24","25-28","29-32"),breaks = c(1:8),limit=c(1,8))+
   scale_y_continuous(name = "% Accuracy",breaks=c(seq(40,90,by=10)),labels = c("","50","","70","","90"))+
   geom_hline(yintercept = 50, color="brown1",linetype="dashed")+
   scale_color_manual(values=color_vec_acc_type, name= "Accuracy Type" )+
   scale_fill_manual(values=color_vec_acc_type, name= "Accuracy Type")+
   ggtitle ("All Participants")+
   theme_classic()+
   theme(axis.title.x = element_text(size = 14,face="bold"),
         axis.title.y = element_text(size = 14,face="bold"),
         axis.text.x = element_text(size = 12,angle=15),
         axis.text.y = element_text(size = 12,angle=0),
         strip.text = element_text(size = 16,face="bold"),
         plot.title=element_text(size = 16,face="bold",hjust=.5),
         legend.position = "none"
         )+
   
   facet_col(~exp_name)
 
)

```

### SM Figure 2 (Right): learning curve with only pre-reg subs & trials
Rerun the same graph but only with those that are pre-registered

```{r prep data for learning curve of acc prereg}

#subject by subject relative accuracy-per relative trial number
learning_curve_acc_prereg_sbs<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,rel_trial_number)%>%
  dplyr::mutate(bin_ind=findInterval(rel_trial_number,seq(1,36,by=4)))%>%
  dplyr::group_by(exp_name,sub_name,bin_ind)%>%
  dplyr::summarize(rel_acc_actual=mean(is_acc)*100,
                   rel_acc_rule=mean(resp_rule_acc)*100)

#all subjects
#pivoting to long and adding a column of acc type
learning_curve_acc_prereg_sbs<-learning_curve_acc_prereg_sbs%>%
  pivot_longer(!c(exp_name,sub_name,bin_ind), names_prefix = "rel_acc_",names_to="type_acc", values_to = "acc_val")


#group statistic-per relative trial number
learning_curve_acc_prereg_grp<-learning_curve_acc_prereg_sbs%>%
  dplyr::group_by(exp_name,bin_ind,type_acc)%>%
  dplyr::summarize(lo_ci=CI(acc_val)[3],hi_ci=CI(acc_val)[1],mean_acc=CI(acc_val)[2])


```


```{r viz learning curve of acc prereg}

#Plot Prereg subjects
#plot learning within block binned by 4 trial 
(
  plot_SM_fig_S2_left<-
  ggplot(data=learning_curve_acc_prereg_grp%>%dplyr::filter(bin_ind<9),aes(x=bin_ind,y=mean_acc, group=type_acc,color=type_acc, fill=type_acc))+
    geom_line()+
    geom_point()+
    geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci),alpha=.3, color=NA)+
    # geom_line(data=sbs_rel_trial_acc_bin,aes(x=bin_ind,y=rel_actual_acc,group=sub_name),alpha=.2)+
    scale_x_continuous(name=" Trial # (in block)", labels = c("1-4","5-8","9-12","13-16","17-20","21-24","25-28","29-32"),breaks = c(1:8),limit=c(1,8))+
   scale_y_continuous(name = "% Accuracy",breaks=c(seq(40,90,by=10)),labels = c("","50","","70","","90"))+
    geom_hline(yintercept = 50, color="brown1",linetype="dashed")+
    scale_color_manual(values=color_vec_acc_type, name= "Accuracy Type" )+
    scale_fill_manual(values=color_vec_acc_type, name= "Accuracy Type")+
    ggtitle ("Pre-Reg Participants")+
   theme_classic()+
   theme(axis.title.x = element_text(size = 14,face="bold"),
         axis.title.y = element_blank(),
         axis.text.x = element_text(size = 12,angle=15),
         axis.text.y = element_text(size = 12,angle=0),
         strip.text = element_text(size = 16,face="bold"),
         plot.title=element_text(size = 16,face="bold",hjust=.5)
         )+
    facet_col(~exp_name)
  
)


# ggsave(plot = plot_SM_fig_S2_left,filename = file.path(path_export_sm_pics,"SM_fig_S2_left.jpg"))
# ggsave(plot = plot_SM_fig_S2_right,filename = file.path(path_export_sm_pics,"SM_fig_S2_right.jpg"))

```


## Fig 2

### Figure 2A right: Gaze follows explicit response-ggpaired
``` {r prep data for looking at  gaze follows prediction  ggpaired (pr)}
#summarizing per trial (pt) and then summing across trials (may be more robust to outliers)
mean_gz_by_pred<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1", "Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,QuestionResult)%>%
  dplyr::summarize(lo_ci=CI(m_gz)[3],hi_ci=CI(m_gz)[1],mean_gz=CI(m_gz)[2])

```

```{r viz gaze follows prediction  ggpaired,fig.show="hold", out.width="50%"}
## plotting paired- for each experiment

#Exp 1!
(
  plot_2b_right<-
    ggpaired(data =mean_gz_by_pred%>%dplyr::filter(exp_name=="Exp. 1"),
             x="QuestionResult", y="mean_gz", id="sub_name", fill="QuestionResult" , line.color = "lightgrey",line.size = .2)+
    # scale_x_discrete(name= "Prediction",labels=c("L","R"))+
    scale_x_discrete(name= "",labels=c("L","R"))+

    ylab("normalized gaze X-axis (z-score)")+
    scale_fill_manual(values=c("plum4","seagreen4"),labels=c("left","right"),name= "Prediction")+
    # ggtitle("Gaze by Prediction (per trial)",
    #         subtitle=sprintf("p: %.3f Cohen's d: %.3f", t.test(data=mean_gz_by_pred, mean_gz~QuestionResult, paired=TRUE)$p.val, 
    #                          cohens_d(data=mean_gz_by_pred%>%ungroup(), mean_gz~QuestionResult, paired=TRUE)$effsize))+
    ylim(c(-.95,.9))+
    theme_classic()+
    theme(axis.title.y = element_blank(),
          axis.title.x = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_blank(),
            # legend.position = "right",
          legend.position = "none",
          )
)


#Exp 2!
(
  plot_2c_right<-
    ggpaired(data =mean_gz_by_pred%>%dplyr::filter(exp_name=="Exp. 2"),
             x="QuestionResult", y="mean_gz", id="sub_name", fill="QuestionResult",line.color = "lightgrey",alpha=.1,line.size = .2 )+
    scale_x_discrete(name= "Prediction",labels=c("L","R"))+
    ylab("normalized gaze X-axis (z-score)")+
    scale_fill_manual(values=c("plum4","seagreen4"),labels=c("left","right"),name= "Prediction")+
    ylim(c(-.95,.9))+
    theme_classic()+
    theme(axis.title.y = element_blank(),
          axis.title.x = element_text(size = 14,face="bold"),
          # axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_blank(),
          # legend.position = "right",
          legend.position = "none",

          )
)

p_built_exp1 <- ggplot_build(plot_2b_right)
p_built_exp2 <- ggplot_build(plot_2c_right)

# Extract x-axis limits
y_limits_exp1 <- p_built_exp1$layout$panel_params[[1]]$y.range
y_limits_exp2 <- p_built_exp2$layout$panel_params[[1]]$y.range

```

```{r get summary stats of gaze by prediction}

#for each experiment seperately
smry_stats_mean_gz_by_pred<-mean_gz_by_pred%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(diff_gz=mean_gz-first(mean_gz))%>%
  dplyr::filter(diff_gz!=0)%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarise(mean_diff=CI(diff_gz)[2],lo_ci=CI(diff_gz)[3],hi_ci=CI(diff_gz)[1],
                   t=t.test(diff_gz)$statistic,df=t.test(diff_gz)$parameter, p.val=t.test(diff_gz)$p.value, ES=one_sample_ttest_cohen_d(diff_gz))





knitr::kable(smry_stats_mean_gz_by_pred,
             digits=2,caption = "Diff gaze direction by prediction  per experiment (pre-reg)")

```

### Figure 2b left: Gaze follows explicit response-timecourse
```{r prep data for vizulization of short time courses splitting trials by PREDICTION}
# binning values used for plotting time course of EM (this requires slim_trkr_prereg_csv)
#single subject
tmcrs_gz_by_pred_df<-slim_trkr_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,TrialNumber)%>%
  dplyr::mutate(bin_ind=findInterval(rel_time_trial,tmcrs_bin_val_shrt))%>%
  dplyr::group_by(exp_name,sub_name,TrialNumber,bin_ind,QuestionResult)%>%
  dplyr::summarize(m_bin_val=mean(z_gz,na.rm = TRUE))%>%
  dplyr::group_by(exp_name,sub_name,QuestionResult,bin_ind)%>%
  dplyr::filter(!is.na(m_bin_val))%>%
  dplyr::group_by(exp_name,sub_name,QuestionResult,bin_ind)%>%
  dplyr::summarise(m_bin=mean(m_bin_val),
                   lo_ci=CI(m_bin_val)[3],
                   hi_ci=CI(m_bin_val)[1],
                   count=n())

# group-all
tmcrs_gz_by_pred_grp_df<-tmcrs_gz_by_pred_df%>%
  dplyr::group_by(exp_name,QuestionResult,bin_ind)%>%
  dplyr::summarize(lo_ci=CI(m_bin)[3],hi_ci=CI(m_bin)[1],m_bin=CI(m_bin)[2])
```

```{r vizulization of short time courses splitting trials by PREDICTION}
### Exp. 1
( 
  plot_2b_left<-ggplot(data=tmcrs_gz_by_pred_grp_df%>%dplyr::filter(exp_name=="Exp. 1"), aes(x=(bin_ind),y=m_bin, color=QuestionResult))+
    geom_line()+
    geom_point()+
    geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci, fill=QuestionResult),alpha=.7,color=NA)+
    scale_fill_manual(name= "Prediction",values=c("plum4","seagreen4"),labels=c("left","right"))+
    scale_color_manual(name= "Prediction",values=c("plum4","seagreen4"),labels=c("left","right"))+
    geom_line(data=tmcrs_gz_by_pred_df%>%filter(QuestionResult=="left")%>%dplyr::filter(exp_name=="Exp. 1"),aes(x=as.numeric(bin_ind),y=m_bin, group=sub_name),color="plum3",alpha=.3)+
    geom_line(data=tmcrs_gz_by_pred_df%>%filter(QuestionResult=="right")%>%dplyr::filter(exp_name=="Exp. 1"),aes(x=as.numeric(bin_ind),y=m_bin, group=sub_name),color="seagreen3",alpha=.3)+
    geom_hline(yintercept = 0, color="black",linetype="dashed")+
    # scale_x_continuous(name="Time [msec]",breaks=c(0,unique(tmcrs_gz_by_pred_df$bin_ind)),labels=tmcrs_bin_val_shrt)+

    # scale_x_continuous(name="Time [msec]",breaks=c(0,unique(tmcrs_gz_by_pred_df$bin_ind)),labels=tmcrs_bin_val_shrt_labels)+
    scale_x_continuous(name="",breaks=c(0,unique(tmcrs_gz_by_pred_df$bin_ind)),labels=tmcrs_bin_val_shrt_labels)+

    labs(y= "Exp. 1",
         # labs(y= " Gaze Direction \n \u2190  left               right \u2192",
         x="")+
    ylim(c(-.95,.9))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.title = element_text(size = 14,face="bold"),
          legend.text = element_text(size = 12,face="bold"),
           legend.position = "none",
          # legend.position = "top"
          )
)

### Exp. 2
( 
  plot_2c_left<-ggplot(data=tmcrs_gz_by_pred_grp_df%>%dplyr::filter(exp_name=="Exp. 2"), aes(x=(bin_ind),y=m_bin, color=QuestionResult))+
    geom_line()+
    geom_point()+
    geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci, fill=QuestionResult),alpha=.7,color=NA)+
    scale_fill_manual(name="Response",values=c("plum4","seagreen4"))+
    scale_color_manual(name="Response",values=c("plum4","seagreen4"))+
    geom_line(data=tmcrs_gz_by_pred_df%>%filter(QuestionResult=="left")%>%dplyr::filter(exp_name=="Exp. 2"),aes(x=as.numeric(bin_ind),y=m_bin, group=sub_name),color="plum3",alpha=.3)+
    geom_line(data=tmcrs_gz_by_pred_df%>%filter(QuestionResult=="right")%>%dplyr::filter(exp_name=="Exp. 2"),aes(x=as.numeric(bin_ind),y=m_bin, group=sub_name),color="seagreen3",alpha=.3)+
    geom_hline(yintercept = 0, color="black",linetype="dashed")+

    scale_x_continuous(name="Time [msec]",breaks=c(0,unique(tmcrs_gz_by_pred_df$bin_ind)),labels=tmcrs_bin_val_shrt_labels)+

 labs(y= "Exp. 2",
     # labs(y= " Gaze Direction \n \u2190  left               right \u2192",   
     x="Time [msec]")+
    ylim(c(-.95,.9))+
theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none")
)


p_built_exp1 <- ggplot_build(plot_2b_right)
p_built_exp2 <- ggplot_build(plot_2c_right)

# Extract x-axis limits
y_limits_exp1 <- p_built_exp1$layout$panel_params[[1]]$y.range
y_limits_exp2 <- p_built_exp2$layout$panel_params[[1]]$y.range

p_built_tmcrs_exp1 <- ggplot_build(plot_2b_left)
p_built_tmcrs_exp2 <- ggplot_build(plot_2c_left)

# Extract x-axis limits
y_limits_tmcrs_exp2 <- p_built_tmcrs_exp2$layout$panel_params[[1]]$y.range

```

Now let's try to combine timecourse and ggpaired using cowplot. 

```{r combine gz by pred timecourse and ggpaired exp 1 }
(
  plot_fig_2B<-plot_grid(plot_2b_left,plot_2b_right, nrow=1,rel_widths = c(2,1),align="v") 
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_2B.pdf"),plot=plot_fig_2B,width=18,height=6,dpi=600, units="cm",device = "pdf")
```


```{r combine gz by pred timecourse and ggpaired exp 2 }
(
  plot_fig_2C<-plot_grid(plot_2c_left,plot_2c_right, nrow=1,rel_widths = c(4,1),align="v") 
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_2C.pdf"),plot=plot_fig_2C,width=24,height=8,dpi=600, units="cm",device = "pdf")
```


### Fig 2B Same/Diff Gaze & Explicit response

Here we are looking at Same/Diff of the eye as binary response
```{r prep data to look at convergence and divergence}
## proportion of each of the categories per subject
porp_eye_resp_same_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1", "Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,eye_resp_match)%>%
  dplyr::summarise(count=n())%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(tot_count=sum(count),
                porp=(count/tot_count)*100)

#getting across experiments
porp_eye_resp_same_acrss_exp<-porp_eye_resp_same_sbs%>%
  dplyr::group_by(eye_resp_match)%>%
  dplyr::summarise(mean_porp=CI(porp)[2],lo_ci=CI(porp)[3],hi_ci=CI(porp)[1])%>%
  dplyr::mutate(exp_name="Exp.1&2")

#per experiment
porp_eye_resp_same_grp_by_exp<-porp_eye_resp_same_sbs%>%
  dplyr::group_by(exp_name,eye_resp_match)%>%
  dplyr::summarise(mean_porp=CI(porp)[2],lo_ci=CI(porp)[3],hi_ci=CI(porp)[1])

#binding
porp_eye_resp_same_grp<-bind_rows(porp_eye_resp_same_grp_by_exp,porp_eye_resp_same_acrss_exp)

knitr::kable(porp_eye_resp_same_grp,digits=2,caption = "Convergence/divergence of Eye & Response")
# #porportion of same
# porp_eye_resp_same_sbs<-join_mean_gz_tbt%>%
#   group_by(sub_name,eye_resp_match)%>%
#   dplyr::summarise(count=n())%>%
#   dplyr::group_by(sub_name)%>%
#   dplyr::mutate(porp=count/sum(count))


```




```{r visualize explicit and eye response same_diff barplot}


(
  plot_fig_2D<-ggplot(porp_eye_resp_same_acrss_exp, aes(x=eye_resp_match, y=mean_porp, fill = eye_resp_match)) + 
    geom_bar(stat="identity", linewidth=2, position=position_dodge(width = .9),width=.5,alpha=0.4) + 
    
     geom_linerange(data=porp_eye_resp_same_acrss_exp,aes(x=eye_resp_match,ymin=lo_ci,ymax=hi_ci), position=position_dodge(width = .9),linewidth=1.5)+
    geom_jitter(data=porp_eye_resp_same_sbs,aes(y=porp,x=eye_resp_match),position=position_jitterdodge(jitter.width=0.15, dodge.width = .9), size = 3,alpha=.3)+
    geom_hline(yintercept = 50, color="brown1",linetype="dashed",linewidth=1.5, alpha=.8)+

    #change y label and limits
    scale_y_continuous(name="% Trials",limits = c(0,100))+
    scale_x_discrete(name="Explicit - Ocular",labels=c("same"="Converge", "diff"="Diverge" ),limits=c("same","diff"))+
    #change legend labels
    scale_fill_manual(values = c("#CCCCCC","#707070"))+
    theme_classic()+
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          legend.position = "none"
    )
)


# ggsave(filename=file.path(path_export_main_pics,"plot_fig_2B_only_line.pdf"),plot=plot_fig_2D,width=12,height=16,dpi=600, units="cm",device = "pdf")
```

We see that around 75% explicit & eye responses are the same, but there is also considerable between subject variance

In a way this is similar to our finding that  Gaze Prediction values are robustly at subject-level  positive.


### Fig 2D: sRW trajectory and Gaze Prediction

First we'll do the pre-reg analysis (individual Ss correlation)
Here we are using sticky RW model. See below for use of pre-registered RW model

```{r prep data for correlation of gaze prediction and sRW traj}

# getting correlation of gaze & RW trajectory (this is done on trial by-trial basis ) per subject
corr_gz_rws_traj_ps<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name!="Exp. 3")%>%
  dplyr::group_by(exp_name,sub_name)%>%
  drop_na(expl.RWS.prev_delta,expl.RWS.dist_v_5)%>%
  dplyr::summarize(
    # corr pred_gz& previous trial's PE
    r.da_pred_gz=rcorr(expl.RWS.prev_delta,m_pred_gz)$r[2],pval.da_pred_gz=rcorr(expl.RWS.prev_delta,m_pred_gz)$P[2], 
    
    #  gaze2prediction & dist of v from 0.5
    r.distv5_pred_gz=rcorr(expl.RWS.dist_v_5,m_pred_gz)$r[2],pval.distv5_pred_gz=rcorr(expl.RWS.dist_v_5,m_pred_gz)$P[2], # corr pred_gz 
    
    #  gaze2prediction & P Choice
    r.PC_pred_gz=rcorr(expl.RWS.p_choice,m_pred_gz)$r[2],pval.PC_pred_gz=rcorr(expl.RWS.p_choice,m_pred_gz)$P[2] 
  )

#pivoting to long (this is done very rudimentary)

#doing for pval
p_val_long_rws<-corr_gz_rws_traj_ps%>%
  select(c(exp_name,sub_name,starts_with("pval")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


# doing for corr
corr_val_long_rws<-corr_gz_rws_traj_ps%>%
  select(c(exp_name,sub_name,starts_with("r")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")

# getting numbeer of sig subjects
sum_p_val_rws=p_val_long_rws%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig,na.rm = TRUE),total_sub=n())

#joining
sum_corr_gz_rws_traj<-corr_val_long_rws%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(mean_corr=CI(val)[2],lo_corr=CI(val)[1],hi_corr=CI(val)[3],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                   ES=one_sample_ttest_cohen_d(val))%>%
  full_join(.,sum_p_val_rws,by=c("exp_name","vars_compared"))
```

print stats of correlation

```{r print stats of gz and rws traj}
knitr::kable(sum_corr_gz_rws_traj%>%dplyr::filter(vars_compared=="PC_pred_gz"),digits = 3, caption = "correlation EM and learning metric RWS ")
```

Now let's make the figures

```{r Fig 2D visualize distribution of correlation value, fig.show="hold", out.width="50%"}
#all subjects
corr_pc_gz2pred_rws<-corr_val_long_rws%>%
  dplyr::filter(vars_compared=="PC_pred_gz")%>%
  dplyr::filter(value_type=="corr")

grp_corr_pc_gz2pred_rws<-corr_pc_gz2pred_rws%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarize(grp_mean=CI(val)[2],lo_ci=CI(val)[1],hi_ci=CI(val)[3])

(
  plot_fig_2D_right<-
    ggplot(data=corr_pc_gz2pred_rws%>%dplyr::filter(exp_name!="Exp. 3"),aes(y=val,x=1))+
        xlim(c(.5,1.5))+
    geom_boxplot(outlier.shape = NA,linewidth=1,color="black",size=.5,width=.4)+ #,width=.02
    geom_point(color="#707070",position = position_jitter(width=.1),size=3, alpha = .8)+
        geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
ylab(expression(atop(rho, "\n Gaze & P. Choice")))+
    # ylab(paste(" \u03C1","Gaze & P. Choice"))+
    ylim(c(-.3,.5))+
    theme_classic()+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          strip.background = element_blank(),
          legend.position = "none"
    )+
    facet_wrap(~exp_name)
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_2D_240624.pdf"),plot=plot_fig_2D_right,width=12,height=16,dpi=600, units="cm",device = "pdf")
```

```{r analyze correlation using lme4 RWS}

#full model
pc_bygz_pred_full_mdl<-expl.RWS.p_choice~m_pred_gz+(1|sub_name)
pc_bygz_pred_full_mdl.res=lmer(pc_bygz_pred_full_mdl,data=mean_gz_prereg_csv,REML = FALSE)

# remove gz prediction
pc_bygz_pred_null_mdl<-expl.RWS.p_choice~1+(1|sub_name)
pc_bygz_pred_null_mdl.res=lmer(pc_bygz_pred_null_mdl,data=mean_gz_prereg_csv,REML = FALSE)

#test with anova
pc_bygz_pred_aov_rws_res<-anova(pc_bygz_pred_full_mdl.res,pc_bygz_pred_null_mdl.res)%>%tidy()

kable(pc_bygz_pred_aov_rws_res,digits=3,caption ="RWS corr Gaze Prediction and P. choice using mixed models")
```



### Fig 2C-  Plotting trajectory of individual Ss

``` {r prep data to plot tbt traj}

rand_sub_name<-"sub3_biu_explor"

## extracting his data
rand_sub_RWS_traj_df<-mean_gz_prereg_csv%>%
  dplyr::filter(sub_name==rand_sub_name)

##rescaling Gaze2Prediction
rand_sub_RWS_traj_df<-rand_sub_RWS_traj_df%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(`Gaze Prediction`=rescale_range(m_pred_gz))%>%
  dplyr::relocate(`Gaze Prediction`,.after="m_pred_gz")%>%
  dplyr::mutate(`P. Choice`=expl.RWS.p_choice)



rand_sub_RWS_traj_long<-rand_sub_RWS_traj_df%>%
  dplyr::select(sub_name,TrialNumber,`Gaze Prediction`, `P. Choice`)%>%
  dplyr::rowwise()%>%
  pivot_longer(c(`Gaze Prediction`, `P. Choice`), values_to="value", names_to="measure")
```


```{r plotting trajectory of Pc and gaze random subject}


 
(
  plot_fig_2C_left<-ggplot(data= rand_sub_RWS_traj_long,aes(x=TrialNumber))+
    # geom_point(aes(y=value,color=measure))+
    geom_line(aes(y=value,color=measure),alpha=.7,linewidth=1.1)+
    geom_point(aes(y=value,color=measure),alpha=.3)+
    geom_vline(xintercept = c(32,64,96,128),alpha=.5,linetype="dashed")+
    scale_color_manual(values=rev(color_vec_eye_expl_source) )+
    # scale_color_discrete( labels=c("\u03B4","cue congruent gaze"))+
    ylab("Value")+
    xlab("Trial Number")+
    scale_x_continuous(expand=c(0,0),breaks=c(0,40,80,120,160),labels=c(as.character(c(0,40,80,120,160))))+
    scale_y_continuous(expand=c(0,0))+

    theme_classic()+
    # ylim(c(0,1))+
    # xlim(c(0,160))+
    # coord_cartesian(xlim = c(0, NA), ylim = c(0, NA)) +  # Adjust viewport without dropping data
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          legend.position = "top",
          legend.title = element_blank(),
          legend.direction = "horizontal",
          legend.text = element_text(size = 14,face="bold"),
          # plot.margin = unit(c(0, 0, 0, 0), "cm")
          # legend.position = "none"
    )
  
  
)  

# ggsave(filename=file.path(path_export_main_pics," plot_fig_2C_left.pdf"),plot= plot_fig_2C_left,width=24,height=12,dpi=600, units="cm",device = "pdf")

```


### Control analysis of Binary GP vs Continous GP

```{r prep data for Binary GP vs Continous GP}
library(ppcor)
library(kableExtra)

df<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name!="Exp. 3")%>%
  dplyr::mutate(gz_pred_binary=if_else(m_pred_gz<0,-1,1))%>%
  dplyr::relocate(gz_pred_binary,.after =m_pred_gz )%>%
  drop_na(gz_pred_binary,m_pred_gz,expl.RWS.p_choice)


subject_correlations <- df %>%
  group_by(sub_name) %>%
  summarize(
    # We extract the 'estimate' (the r value) from the pcor.test result
    partial_r = pcor.test(x = expl.RWS.p_choice, 
                          y = m_pred_gz, 
                          z = gz_pred_binary, 
                          method = "pearson")$estimate
  )


# 2. Transform r to z for normality
subject_correlations <- subject_correlations %>%
  mutate(fisher_z = atanh(partial_r)) # atanh is the Fisher Z transform in R

# 3. Perform a one-sample t-test on the Fisher Z scores
group_test <- t.test(subject_correlations$fisher_z, mu = 0)

d_effect <- subject_correlations %>% 
  cohens_d(fisher_z ~ 1, mu = 0)

# 4.displaying
# Create a display table using your existing objects
results_table <- data.frame(
  Variable = "Fisher Z (Choice ~ Gaze)",
  Mean = group_test$estimate,
  t = group_test$statistic,
  df = group_test$parameter,
  p = group_test$p.value,
  d = d_effect$effsize
)

# Render the kable table
results_table %>%
  mutate(across(where(is.numeric), ~ round(., 3))) %>%
  mutate(p = if_else(p < .001, "< .001", as.character(p))) %>%
  rename(`$t$` = t, `$df$` = df, `$p$` = p, `$d$` = d) %>%
  kable(escape = FALSE, booktabs = TRUE, align = "c", 
        caption = "Group-Level Statistical Analysis of CGP vs GGP") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE)

```


Try with multiple regression gives a similar result
```{r}
subject_models_r2 <- df %>%
  group_by(sub_name) %>%
  nest() %>%
  dplyr::mutate(
    # Fit the Null Model
    mod_null = map(data, ~lm(expl.RWS.p_choice ~ gz_pred_binary, data = .x)),
    # Fit the Full Model
    mod_full = map(data, ~lm(expl.RWS.p_choice ~ gz_pred_binary + m_pred_gz, data = .x)),
    
    # Extract R-squared using glance
    r2_null = map_dbl(mod_null, ~glance(.x)$r.squared),
    r2_full = map_dbl(mod_full, ~glance(.x)$r.squared)
  )%>%
  dplyr::mutate(r2_diff = r2_full - r2_null) %>%
  dplyr::select(sub_name, r2_null, r2_full, r2_diff)

t_test_res <- t.test(subject_models_r2$r2_diff, mu = 0)
print(t_test_res)

subject_models_r2%>%dplyr::ungroup()%>%cohens_d(r2_diff~1,mu=0)

subject_models_r2%>%dplyr::ungroup()%>%get_summary_stats(r2_diff,type = "mean_ci")
```



## SM Figures:S3, S4, S6 
### Fig S3: Individual Subject Gaze by Prediction 
```{r prep data for SM fig 3}
#fix up subjects name
mean_gz_by_pred<-mean_gz_by_pred%>%
  dplyr::mutate(new_sub_name=sprintf("Sub %.2d",parse_number(sub_name)))

( plot_SM_fig_S3<-
    ggplot(data=mean_gz_by_pred,aes(x=mean_gz,y=new_sub_name,color=as.factor(QuestionResult)))+ #y=fct_reorder(sub_name, desc(sub_num)
    geom_pointrange(aes(xmin=lo_ci,xmax=hi_ci),position=position_dodge(width = .3))+
    geom_vline(xintercept = 0,color="brown1",linetype="dashed")+
    scale_color_manual(name="Prediction",values=c("plum4","seagreen4"),labels=c("left","right"))+
    facet_col(~exp_name,scales = "free_y")+
    ylab("Subject")+
    xlab("Gaze Direction")+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 8,angle=0),
          )
  # ggtitle("Gaze by Prediction ")
)
# ggsave(plot = plot_SM_fig_S3,filename = file.path(path_export_sm_pics,"SM_fig_S3.jpg"))

```

Now let's do the stats
```{r run stats of individual subjects}

gz_by_pred_stats<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarise(p=t.test(m_gz~QuestionResult)$p.value,
                   is_sig=if_else(p<.05,1,0))

gz_by_pred_stats_per_exp<-gz_by_pred_stats%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarise(n_sig=sum(is_sig), total_n=n())

kable(gz_by_pred_stats_per_exp,caption = "Gaze by Prediction, single ss signfiacne")

```


### SM Fig 4 convergence and dvergence per experiment

```{r prep data to look at convergence and divergence per exp all exp}
## proportion of each of the categories per subject
porp_eye_resp_same_sbs_all_exp<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,eye_resp_match)%>%
  dplyr::summarise(count=n())%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(tot_count=sum(count),
                porp=(count/tot_count)*100)



#per experiment
porp_eye_resp_same_grp_by_exp<-porp_eye_resp_same_sbs_all_exp%>%
  dplyr::group_by(exp_name,eye_resp_match)%>%
  dplyr::summarise(mean_porp=CI(porp)[2],lo_ci=CI(porp)[3],hi_ci=CI(porp)[1])

```

```{r viz convergence and divergence per exp all exp}

(
  plot_SM_fig_S4<-ggplot(porp_eye_resp_same_grp_by_exp, aes(x=eye_resp_match, y=mean_porp, fill = eye_resp_match)) + 
    geom_bar(stat="identity", linewidth=2, position=position_dodge(width = .9),width=.5, color="black",alpha=0.4) + 
    
    geom_errorbar(data=porp_eye_resp_same_grp_by_exp,aes(x=eye_resp_match,ymin=lo_ci,ymax=hi_ci), position=position_dodge(width = .9),width=.4,linewidth=1.5,)+
    geom_jitter(data=porp_eye_resp_same_sbs_all_exp,aes(y=porp,x=eye_resp_match),position=position_jitterdodge(jitter.width=0.2, dodge.width = .9), size = 3,alpha=.5)+ 
    geom_hline(yintercept = 50, color="brown1",linetype="dashed",linewidth=1.5, alpha=.8)+
    
    #change y label and limits
    scale_y_continuous(name="% Trials",limits = c(0,100))+
    scale_x_discrete(name="Explicit - Ocular",labels=c("same"="Converge", "diff"="Diverge" ),limits=c("same","diff"))+
    #change legend labels
    scale_fill_manual(values = c("#CCCCCC","#707070"))+
    theme_classic()+
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          legend.position = "none",
          strip.text = element_text(size = 16,face="bold"),
          strip.background = element_blank()

    )+
    facet_wrap(~exp_name)
)

# ggsave(plot = plot_SM_fig_S4,filename = file.path(path_export_sm_pics,"SM_fig_S4_converge_diverge.jpg"))

```


### SM Fig S6  P. Choice from RW & corr to Gaze Prediction
```{r prep data for correlation of gaze prediction and RW traj}

# getting correlation of gaze & RW trajectory (this is done on trial by-trial basis ) per subject
corr_gz_rw_traj_ps<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(
    # corr pred_gz& previous trial's PE
    r.da_pred_gz=rcorr(expl.RW.prev_delta,m_pred_gz)$r[2],pval.da_pred_gz=rcorr(expl.RW.prev_delta,m_pred_gz)$P[2], 
    
    #  gaze2prediction & dist of v from 0.5
    r.distv5_pred_gz=rcorr(expl.RW.dist_v_5,m_pred_gz)$r[2],pval.distv5_pred_gz=rcorr(expl.RW.dist_v_5,m_pred_gz)$P[2], # corr pred_gz 
    
    #  gaze2prediction & P Choice
    r.PC_pred_gz=rcorr(expl.RW.p_choice,m_pred_gz)$r[2],pval.PC_pred_gz=rcorr(expl.RW.p_choice,m_pred_gz)$P[2] 
  )


#pivoting to long (this is done very rudimentary)

#doing for pval
p_val_long_rw<-corr_gz_rw_traj_ps%>%
  dplyr::select(c(exp_name,sub_name,starts_with("pval")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


# doing for corr
corr_val_long_rw<-corr_gz_rw_traj_ps%>%
  dplyr::select(c(exp_name,sub_name,starts_with("r")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")

# getting numbeer of sig subjects
sum_p_val_rw=p_val_long_rw%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig),total_sub=n())

#joining
sum_corr_gz_rw_traj<-corr_val_long_rw%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(mean_corr=CI(val)[2],lo_corr=CI(val)[1],hi_corr=CI(val)[3],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                   ES=one_sample_ttest_cohen_d(val))%>%
  full_join(.,sum_p_val_rw,by=c("exp_name","vars_compared"))
```

print stats of pre-reg analysis
```{r print stats of gz and rw traj}
knitr::kable(sum_corr_gz_rw_traj,digits = 3, caption = "correlation EM and learning metric RW (PreReged)")
```

Checking with a mixed model

```{r analyze correlation using lme4 RW}

#full model
pc_bygz_pred_full_mdl<-expl.RW.p_choice~m_pred_gz+(1|sub_name)
pc_bygz_pred_full_mdl.res_rw=lmer(pc_bygz_pred_full_mdl,data=mean_gz_prereg_csv,REML = FALSE)

# remove gz prediction
pc_bygz_pred_null_mdl<-expl.RW.p_choice~1+(1|sub_name)
pc_bygz_pred_null_mdl.res_rw=lmer(pc_bygz_pred_null_mdl,data=mean_gz_prereg_csv,REML = FALSE)

#test with anova
pc_bygz_pred_aov_res_rw<-anova(pc_bygz_pred_full_mdl.res_rw,pc_bygz_pred_null_mdl.res_rw)%>%tidy()

kable(pc_bygz_pred_aov_res_rw,digits=3,caption="RW")
```


So lme gives simialr signfiacnt results using RW model. 


```{r viz figure S6 gz and P choice correlation}

corr_pc_gz2pred_rw<-corr_val_long_rw%>%
  dplyr::filter(vars_compared=="PC_pred_gz")%>%
  dplyr::filter(value_type=="corr")

grp_corr_pc_gz2pred_rw<-corr_pc_gz2pred_rw%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarize(grp_mean=CI(val)[2],lo_ci=CI(val)[1],hi_ci=CI(val)[3])

(
  plot_SM_fig_S6<-
    ggplot(data=corr_pc_gz2pred_rw%>%dplyr::filter(exp_name!="Exp. 3"),aes(y=val,x=1))+
    # xlim(c(.8,1.2))+
    geom_violin(alpha=.4,scale="width")+
    # geom_boxplot(aplha=.4)+ #,width=.02
    geom_pointrange (data=grp_corr_pc_gz2pred_rw%>%dplyr::filter(exp_name!="Exp. 3"), aes(y=grp_mean,ymin=lo_ci, ymax=hi_ci),size=3,fatten=1.5, color="black")+
    geom_point(color="darkgrey",position = position_jitter(width=.05),size=2.5, alpha = .6)+
    
    # geom_hline(yintercept = 0, color="red",linetype="solid",size=1.5)+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed")+
ylab(expression(atop(rho, "\n Gaze & P. Choice")))+
    # ylab(paste(" \u03C1","Gaze & P. Choice"))+
    ylim(c(-.3,.5))+
    
    theme_classic()+
    # coord_fixed(ratio = 4,xlim = c(0.8, 1.2))+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          legend.position = "none"
    )+
    facet_wrap(~exp_name)
)

# ggsave(filename=file.path(path_export_sm_pics,"plot_SM_fig_S6.png"),plot=plot_SM_fig_S6,dpi=600, units="cm",device = "png")

```



## Figure 3

Examining confidence benchmarks

### Panel A: Benchamrk 1  montonic rise in acc
```{r prep data for benchmark 1 check if accuarcy increases with gaze2prediction}

#add percentile 
mean_gz_prereg_csv<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(tile_gz2pred=ntile(m_pred_gz,n_ptiles_gz2pred))%>%
  dplyr::relocate(tile_gz2pred,.after = m_pred_gz)

#get subject by subject
sbs_acc_per_tile_gz2pred<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,tile_gz2pred)%>%
  dplyr::summarize(m_actual_acc=mean(is_acc)*100,m_rule_acc=mean(resp_rule_acc)*100,m_gz2pred=mean(m_pred_gz),count=n())


#group- all subjects
grp_acc_per_tile_gz2pred<-sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,tile_gz2pred)%>%
  dplyr::summarize(lo_ci_act_acc=CI(m_actual_acc)[1],hi_ci_act_acc=CI(m_actual_acc)[3],m_actual_acc=CI(m_actual_acc)[2],
                   lo_ci_rule_acc=CI(m_rule_acc)[1],hi_ci_rule_acc=CI(m_rule_acc)[3],m_rule_acc=CI(m_rule_acc)[2])


```

```{r run prereg stats for benchmark 1}

# getting correlation of gaze & ACC (this is done on trial by-trial basis ) per subject
sbs_corr_bench1_acc_gz_pred<-sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(
    # corr rule acc & gz prediction
    r.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$r[2],pval.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$P[2]
  )%>%
  dplyr::mutate(is_sig=if_else(pval.acc_gz_pred<.05,1,0))



#joining
sum_stats_corr_bench1_acc_gz_pred <-sbs_corr_bench1_acc_gz_pred%>%
  group_by(exp_name)%>%
  dplyr::summarise(mean_corr=CI(r.acc_gz_pred)[2],lo_corr=CI(r.acc_gz_pred)[1],hi_corr=CI(r.acc_gz_pred)[3],
                   group_t_statistic=t.test(r.acc_gz_pred)$statistic, group_pval=t.test(r.acc_gz_pred)$p.value,
                   ES=one_sample_ttest_cohen_d(r.acc_gz_pred))

knitr::kable(sum_stats_corr_bench1_acc_gz_pred,digits=4, caption = "Conf benchmark 1 distribution of spearman correlation")
```

So these results aren't super strong. But this is actually a pretty poor way of testing this hypothesis. 

Let's try now using a logistic regression approach

```{r test confidence benchmark 1 with glmer}
## RE: geberal intercept
rule_acc_by_gz_pred_frmla<-resp_rule_acc~m_pred_gz+(1|sub_name)

rule_acc_by_gz_pred.res_exp1=glmer(rule_acc_by_gz_pred_frmla,data=mean_gz_prereg_csv%>%dplyr::filter(exp_name=="Exp. 1"),
                                   family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")


rule_acc_by_gz_pred.res_exp2=glmer(rule_acc_by_gz_pred_frmla,data=mean_gz_prereg_csv%>%dplyr::filter(exp_name=="Exp. 2"),
                                   family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 2")

knitr::kable(bind_rows(rule_acc_by_gz_pred.res_exp1,rule_acc_by_gz_pred.res_exp2)%>%
               dplyr::filter(!is.na(p.value)), digits = 5, caption="Conf benchmark 1 with glmer")

```

So this gives a really robust result that is also statistically much more appropriate. 

Visualize Panel A: benchmark 1 (Right= Exp. 1 Left Exp. 2)

```{r visualize Fig 3A benchmark 1 check if accuarcy increases with gaze2prediction, fig.show="hold", out.width="50%" }
# plot rule acc  
##Exp. 1
(plot_fig_3A_exp1<-
   ggplot(data=grp_acc_per_tile_gz2pred%>%dplyr::filter(exp_name=="Exp. 1"),aes(x=tile_gz2pred, y= m_rule_acc))+
   geom_pointrange(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),color="black",linewidth=1.5)+
    geom_line(alpha=.8,linewidth=2,color="black")+
   geom_point(size=3)+
   # geom_ribbon(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),fill="sandybrown", alpha=.2,  color=NA)+
   
   scale_x_continuous(name= ("Gaze Prediction"))+
   scale_y_continuous(name=("% Correct"),limits = c(62,86))+
   
   theme_classic()+
   theme(axis.title.x = element_text(size = 16,face="bold"),
         axis.title.y = element_text(size = 16,face="bold"),
         axis.text.x = element_text(size = 14,angle=0),
         axis.text.y = element_text(size = 14,angle=0),
         legend.position = "none"
   )
)

##Exp. 2
(plot_fig_3A_exp2<-
    ggplot(data=grp_acc_per_tile_gz2pred%>%dplyr::filter(exp_name=="Exp. 2"),aes(x=tile_gz2pred, y= m_rule_acc))+
    geom_pointrange(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),color="black",linewidth=1.5)+
    geom_line(alpha=.8,linewidth=2,color="black")+
    geom_point(size=3)+
    # geom_ribbon(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),fill="sandybrown", alpha=.2,  color=NA)+
    scale_x_continuous(name= ("Gaze Prediction"))+
    scale_y_continuous(name=("% Correct"),limits = c(62,86))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
         
          legend.position = "none"
    )
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3A_exp1.pdf"),plot=plot_fig_3A_exp1,device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3A_exp2.pdf"),plot=plot_fig_3A_exp2,device = "pdf")
```


### Panel B: Benchmark 2 - folded X pattern

We are  binning by expectation strength & rule accuracy 

Here again we can do either with RW or RWS 

#### Running with RWS
```{r prep data to look at benchmark 2 of confidence using distV as proxy of evidence RWS}
n_ptiles_dist_v<-6

gz_by_distV_RWS_acc_df<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,resp_rule_acc)%>%
  dplyr::mutate(dist_v_rule_acc_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning according to RULE ACC
  dplyr::relocate(dist_v_rule_acc_bin,.after="expl.RW.dist_v_5") %>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning only according to V
  dplyr::relocate(dist_v_bin,.after="dist_v_rule_acc_bin") 
```


```{r run prereg stats for Benchmark 2 using lme4 RWS }
#here 
#Exp 1
bench2_full_frmla<-m_pred_gz~resp_rule_acc+dist_v_rule_acc_bin+resp_rule_acc:dist_v_rule_acc_bin+(1|sub_name)
# bench2_full_frmla<-m_pred_gz~resp_rule_acc+expl.dist_v_5+resp_rule_acc:expl.dist_v_5+(1|sub_name)

bench2_full_exp1.res_rws=lmer(bench2_full_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 1"),REML = FALSE)



# remove interaction term
bench2_null_frmla<-m_pred_gz~resp_rule_acc+dist_v_rule_acc_bin+(1|sub_name)
# bench2_null_frmla<-m_pred_gz~resp_rule_acc+expl.dist_v_5+(1|sub_name)

bench2_null_exp1.res_rws=lmer(bench2_null_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 1"),REML = FALSE)


#test with anova
bench2_aov_exp1_res_rws<-anova(bench2_full_exp1.res_rws,bench2_null_exp1.res_rws)%>%tidy()%>%mutate(exp = "Exp. 1")%>%dplyr::filter(!is.na(df))

# Exp 2. 
bench2_full_exp2.res_rws=lmer(bench2_full_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 2"),REML = FALSE)
bench2_null_exp2.res_rws=lmer(bench2_null_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 2"),REML = FALSE)

bench2_aov_exp2_res_rws<-anova(bench2_full_exp2.res_rws,bench2_null_exp2.res_rws)%>%tidy()%>%mutate(exp = "Exp. 2")%>%dplyr::filter(!is.na(df))

knitr::kable(bind_rows(bench2_aov_exp1_res_rws,bench2_aov_exp2_res_rws), digits= 4, caption= "RWS lme results Benchmark 2")
```

```{r getting summary stats for visualization bin by v  and acc RWS}
# summarizing across subjects
gz_by_distV_acc_grp_rws<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  dplyr::group_by(exp_name,dist_v_rule_acc_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2],n_sub=n())

```


```{r visualize benchmark 2 for Acc as functioon of gaze confidence & v binn using v and acc RWS, fig.show="hold", out.width="50%" }
#visualize rule acc
(
  plot_fig_3B_exp1<-
    ggplot(data=gz_by_distV_acc_grp_rws%>%dplyr::filter(exp_name=="Exp. 1"),
           aes(x=(dist_v_rule_acc_bin),y=m_gz2pred,color=as.factor(acc),fill=as.factor(acc), group=as.factor(acc)))+
    geom_line(aes(color=as.factor(acc)),alpha=.4,linewidth=2)+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_rule_acc_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    scale_x_continuous(name=" Expectation Strength")+
    scale_y_continuous(name = "Gaze Prediction")+
    scale_color_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    scale_fill_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    theme_classic()+
    theme(plot.title = element_text(size = 20,face="bold",hjust = 0.5),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none"
    )
)

## Exp. 2
(
  plot_fig_3B_exp2<-
    ggplot(data=gz_by_distV_acc_grp_rws%>%dplyr::filter(exp_name=="Exp. 2"),
           aes(x=(dist_v_rule_acc_bin),y=m_gz2pred,color=as.factor(acc),fill=as.factor(acc), group=as.factor(acc)))+
    geom_line(aes(color=as.factor(acc)),alpha=.4,linewidth=2)+
    # geom_point(aes(color=as.factor(acc)))+
    # geom_ribbon(aes(ymin=lo_ci,ymax=hi_ci,fill=as.factor(acc),group=as.factor(acc)), alpha=.2,colour = NA)+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_rule_acc_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    scale_x_continuous(name=" Expectation Strength")+
    scale_y_continuous(name = "Gaze Prediction")+
    scale_color_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    scale_fill_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    # ggtitle("Gaze2Pred diverges  by\n expectation strength & Acc")+
    theme_classic()+
    theme(plot.title = element_text(size = 20,face="bold",hjust = 0.5),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none"
    )
)


# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3B_exp1.pdf"),plot=plot_fig_3B_exp1,width=16,height=16,dpi=600, units="cm",device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3B_exp2.pdf"),plot=plot_fig_3B_exp2,width=16,height=16,dpi=600, units="cm",device = "pdf")

```

```{r get statistic tables of benchmark 2 pairwise comparisons RWS}
#getting summary
smry_vals_gz_by_distV_RWS_acc_pairwise<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  # dplyr::group_by(sub_name)%>%
  # dplyr::filter(n()!=12)%>%
  dplyr::group_by(exp_name,dist_v_rule_acc_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2])%>%
  pivot_wider(names_from = acc, values_from = c(lo_ci,hi_ci,m_gz2pred))

#get stats
stats_gz_by_distV_RWS_acc_pairwise<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin)%>%
  dplyr::filter(n()==2 )%>% #removing Ss with less than 5 items per bin
  dplyr::group_by(exp_name,dist_v_rule_acc_bin)%>%
  
  dplyr::summarise(p_val=t.test(m_gz2pred~acc,paired = TRUE)$p.value,
                   t=t.test(m_gz2pred~acc,paired = TRUE)$statistic,
                   df=t.test(m_gz2pred~acc,paired = TRUE)$parameter)

#joining
smry_gz_by_distV_RWS_acc_pairwise<-full_join(smry_vals_gz_by_distV_RWS_acc_pairwise,
                                             stats_gz_by_distV_RWS_acc_pairwise,
                                             by=c("exp_name","dist_v_rule_acc_bin")
                                             
)

knitr::kable(smry_gz_by_distV_RWS_acc_pairwise,digits=4,caption="SM table B2 pairise comparison of Benchmark 2 RWS")

```

```{r run pairwise comparison of Bench 2 RWS }
sbs_bench2_RWS<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  # dplyr::filter(count>4)%>% # Currently not filtering out subjects except those without any values in bin
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==12)

pwc_bench_2_RWS <- sbs_bench2_RWS %>% 
  ungroup()%>%
  group_by(dist_v_rule_acc_bin) %>%
  pairwise_t_test(
    m_gz2pred ~ acc, paired = TRUE,
    p.adjust.method = "bonferroni"
    )%>%dplyr::select(dist_v_rule_acc_bin,statistic,df,p,p.adj)%>%
  dplyr::mutate(model="sRW")


```


### Fig 3C: Benchmark 3 - steeper curve for high Gaze prediction trials
#### RWS
```{r benchmark 3: prep data to look at  of confidence using distV RWS as proxy of evidence}
# binning prediction gz streng
acc_by_gz_distV_RWS_sbs<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  drop_na(dist_v_bin)%>%
  dplyr::group_by(exp_name,sub_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarize(acc=mean(resp_rule_acc),count=n()) 

# summarizing across subject
acc_by_gz_distV_RWS_grp<-acc_by_gz_distV_RWS_sbs%>%
  dplyr::group_by(exp_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarise(lo_ci=CI(acc)[1]*100,hi_ci=CI(acc)[3]*100,m_acc=CI(acc)[2]*100)



```


```{r visualize benchmark 3 for gaze as confidence using V RWS as proxy of evidence, fig.show="hold", out.width="50%" }

#define colors for high/low gaze prediction
cvec_pred_strength<-c("black","azure3")


#Experiment 1
( plot_fig_3C_exp1<-
    ggplot(acc_by_gz_distV_RWS_grp%>%dplyr::filter(exp_name=="Exp. 1"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none"
         )
    )


#Experiment 2
(plot_fig_3C_exp2<-
    ggplot(acc_by_gz_distV_RWS_grp%>%dplyr::filter(exp_name=="Exp. 2"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = c(.9,.2)
         )
)


# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3C_exp1.pdf"),plot=plot_fig_3C_exp1,width=16,height=16,dpi=600, units="cm",device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3C_exp2.pdf"),plot=plot_fig_3C_exp2,width=16,height=16,dpi=600, units="cm",device = "pdf")
```

```{r prep data to run prereg stats for Benchmark 3 using lme4  bin only by v5 RWS}
acc_w_gz_distV_RWS_sbs_4stats<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  dplyr::select("exp_name","sub_name","TrialNumber","resp_rule_acc", "pred_gz_bin","dist_v_bin")


```

```{r run prereg stats for Benchmark 3 using lme4  bin only by v5 RWS glmer}
bench3_full_frmla<-resp_rule_acc~pred_gz_bin+dist_v_bin+pred_gz_bin:dist_v_bin+(1|sub_name)

#Exp 1
bench3_full_exp1.res_rws=glmer(bench3_full_frmla,                        
                               data=acc_w_gz_distV_RWS_sbs_4stats%>%filter(exp_name=="Exp. 1")%>%ungroup(),
                               family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")


# Exp 2
bench3_full_exp2.res_rws=glmer(bench3_full_frmla,                        
                               data=acc_w_gz_distV_RWS_sbs_4stats%>%filter(exp_name=="Exp. 2")%>%ungroup(),
                               family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 2")

knitr::kable(bind_rows(bench3_full_exp1.res_rws,bench3_full_exp2.res_rws)%>%dplyr::filter(effect=="fixed"),caption = "Benchmark 3 RWS (glmer)")
```

```{r pairwise comparison of Bench 3 RWS}
sbs_bench3_RWS<-acc_w_gz_distV_RWS_sbs_4stats%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,pred_gz_bin,dist_v_bin)%>%
  dplyr::summarise(m_acc=mean(resp_rule_acc)*100,count=n())%>%
  # dplyr::filter(count>4)%>% # Currently not filtering out subjects except those without any values in bin
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==12)

pwc_bench_3_RWS <- sbs_bench3_RWS %>% 
  ungroup()%>%
  group_by(dist_v_bin) %>%
  pairwise_t_test(
    m_acc ~ pred_gz_bin, paired = TRUE,
    p.adjust.method = "bonferroni"
    )%>%
  dplyr::select(dist_v_bin,statistic,df,p,p.adj)%>%
  dplyr::mutate(model="RWS")
```


### Additional anaylses on Folded X pattern

## Figure 3

Examining confidence benchmarks

### Panel A: Benchamrk 1  montonic rise in acc
```{r prep data for benchmark 1 check if accuarcy increases with gaze2prediction}

#add percentile 
mean_gz_prereg_csv<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(tile_gz2pred=ntile(m_pred_gz,n_ptiles_gz2pred))%>%
  dplyr::relocate(tile_gz2pred,.after = m_pred_gz)

#get subject by subject
sbs_acc_per_tile_gz2pred<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,tile_gz2pred)%>%
  dplyr::summarize(m_actual_acc=mean(is_acc)*100,m_rule_acc=mean(resp_rule_acc)*100,m_gz2pred=mean(m_pred_gz),count=n())


#group- all subjects
grp_acc_per_tile_gz2pred<-sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,tile_gz2pred)%>%
  dplyr::summarize(lo_ci_act_acc=CI(m_actual_acc)[1],hi_ci_act_acc=CI(m_actual_acc)[3],m_actual_acc=CI(m_actual_acc)[2],
                   lo_ci_rule_acc=CI(m_rule_acc)[1],hi_ci_rule_acc=CI(m_rule_acc)[3],m_rule_acc=CI(m_rule_acc)[2])


```

```{r run prereg stats for benchmark 1}

# getting correlation of gaze & ACC (this is done on trial by-trial basis ) per subject
sbs_corr_bench1_acc_gz_pred<-sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(
    # corr rule acc & gz prediction
    r.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$r[2],pval.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$P[2]
  )%>%
  dplyr::mutate(is_sig=if_else(pval.acc_gz_pred<.05,1,0))



#joining
sum_stats_corr_bench1_acc_gz_pred <-sbs_corr_bench1_acc_gz_pred%>%
  group_by(exp_name)%>%
  dplyr::summarise(mean_corr=CI(r.acc_gz_pred)[2],lo_corr=CI(r.acc_gz_pred)[1],hi_corr=CI(r.acc_gz_pred)[3],
                   group_t_statistic=t.test(r.acc_gz_pred)$statistic, group_pval=t.test(r.acc_gz_pred)$p.value,
                   ES=one_sample_ttest_cohen_d(r.acc_gz_pred))

knitr::kable(sum_stats_corr_bench1_acc_gz_pred,digits=4, caption = "Conf benchmark 1 distribution of spearman correlation")
```

So these results aren't super strong. But this is actually a pretty poor way of testing this hypothesis. 

Let's try now using a logistic regression approach

```{r test confidence benchmark 1 with glmer}
## RE: geberal intercept
rule_acc_by_gz_pred_frmla<-resp_rule_acc~m_pred_gz+(1|sub_name)

rule_acc_by_gz_pred.res_exp1=glmer(rule_acc_by_gz_pred_frmla,data=mean_gz_prereg_csv%>%dplyr::filter(exp_name=="Exp. 1"),
                                   family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")


rule_acc_by_gz_pred.res_exp2=glmer(rule_acc_by_gz_pred_frmla,data=mean_gz_prereg_csv%>%dplyr::filter(exp_name=="Exp. 2"),
                                   family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 2")

knitr::kable(bind_rows(rule_acc_by_gz_pred.res_exp1,rule_acc_by_gz_pred.res_exp2)%>%
               dplyr::filter(!is.na(p.value)), digits = 5, caption="Conf benchmark 1 with glmer")

```

So this gives a really robust result that is also statistically much more appropriate. 

Visualize Panel A: benchmark 1 (Right= Exp. 1 Left Exp. 2)

```{r visualize Fig 3A benchmark 1 check if accuarcy increases with gaze2prediction, fig.show="hold", out.width="50%" }
# plot rule acc  
##Exp. 1
(plot_fig_3A_exp1<-
   ggplot(data=grp_acc_per_tile_gz2pred%>%dplyr::filter(exp_name=="Exp. 1"),aes(x=tile_gz2pred, y= m_rule_acc))+
   geom_pointrange(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),color="black",linewidth=1.5)+
    geom_line(alpha=.8,linewidth=2,color="black")+
   geom_point(size=3)+
   # geom_ribbon(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),fill="sandybrown", alpha=.2,  color=NA)+
   
   scale_x_continuous(name= ("Gaze Prediction"))+
   scale_y_continuous(name=("% Correct"),limits = c(62,86))+
   
   theme_classic()+
   theme(axis.title.x = element_text(size = 16,face="bold"),
         axis.title.y = element_text(size = 16,face="bold"),
         axis.text.x = element_text(size = 14,angle=0),
         axis.text.y = element_text(size = 14,angle=0),
         legend.position = "none"
   )
)

##Exp. 2
(plot_fig_3A_exp2<-
    ggplot(data=grp_acc_per_tile_gz2pred%>%dplyr::filter(exp_name=="Exp. 2"),aes(x=tile_gz2pred, y= m_rule_acc))+
    geom_pointrange(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),color="black",linewidth=1.5)+
    geom_line(alpha=.8,linewidth=2,color="black")+
    geom_point(size=3)+
    # geom_ribbon(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),fill="sandybrown", alpha=.2,  color=NA)+
    scale_x_continuous(name= ("Gaze Prediction"))+
    scale_y_continuous(name=("% Correct"),limits = c(62,86))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
         
          legend.position = "none"
    )
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3A_exp1.pdf"),plot=plot_fig_3A_exp1,device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3A_exp2.pdf"),plot=plot_fig_3A_exp2,device = "pdf")
```


### Panel B: Benchmark 2 - folded X pattern

We are  binning by expectation strength & rule accuracy 


```{r prep data to look at benchmark 2 of confidence using distV as proxy of evidence RWS}
n_ptiles_dist_v<-6

gz_by_distV_RWS_acc_df<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name,resp_rule_acc)%>%
  dplyr::mutate(dist_v_rule_acc_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning according to RULE ACC
  dplyr::relocate(dist_v_rule_acc_bin,.after="expl.RW.dist_v_5") %>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning only according to V
  dplyr::relocate(dist_v_bin,.after="dist_v_rule_acc_bin") 
```


```{r run prereg stats for Benchmark 2 using lme4 RWS }
#here 
#Exp 1
bench2_full_frmla<-m_pred_gz~resp_rule_acc+dist_v_rule_acc_bin+resp_rule_acc:dist_v_rule_acc_bin+(1|sub_name)
# bench2_full_frmla<-m_pred_gz~resp_rule_acc+expl.dist_v_5+resp_rule_acc:expl.dist_v_5+(1|sub_name)

bench2_full_exp1.res_rws=lmer(bench2_full_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 1"),REML = FALSE)



# remove interaction term
bench2_null_frmla<-m_pred_gz~resp_rule_acc+dist_v_rule_acc_bin+(1|sub_name)
# bench2_null_frmla<-m_pred_gz~resp_rule_acc+expl.dist_v_5+(1|sub_name)

bench2_null_exp1.res_rws=lmer(bench2_null_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 1"),REML = FALSE)


#test with anova
bench2_aov_exp1_res_rws<-anova(bench2_full_exp1.res_rws,bench2_null_exp1.res_rws)%>%tidy()%>%mutate(exp = "Exp. 1")%>%dplyr::filter(!is.na(df))

# Exp 2. 
bench2_full_exp2.res_rws=lmer(bench2_full_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 2"),REML = FALSE)
bench2_null_exp2.res_rws=lmer(bench2_null_frmla,data=gz_by_distV_RWS_acc_df%>%filter(exp_name=="Exp. 2"),REML = FALSE)

bench2_aov_exp2_res_rws<-anova(bench2_full_exp2.res_rws,bench2_null_exp2.res_rws)%>%tidy()%>%mutate(exp = "Exp. 2")%>%dplyr::filter(!is.na(df))

knitr::kable(bind_rows(bench2_aov_exp1_res_rws,bench2_aov_exp2_res_rws), digits= 4, caption= "RWS lme results Benchmark 2")
```

```{r getting summary stats for visualization bin by v  and acc RWS}
# summarizing across subjects
gz_by_distV_acc_grp_rws<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  dplyr::group_by(exp_name,dist_v_rule_acc_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2],n_sub=n())

```


```{r visualize benchmark 2 for Acc as functioon of gaze confidence & v binn using v and acc RWS, fig.show="hold", out.width="50%" }
#visualize rule acc
(
  plot_fig_3B_exp1<-
    ggplot(data=gz_by_distV_acc_grp_rws%>%dplyr::filter(exp_name=="Exp. 1"),
           aes(x=(dist_v_rule_acc_bin),y=m_gz2pred,color=as.factor(acc),fill=as.factor(acc), group=as.factor(acc)))+
    geom_line(aes(color=as.factor(acc)),alpha=.4,linewidth=2)+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_rule_acc_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    scale_x_continuous(name=" Expectation Strength")+
    scale_y_continuous(name = "Gaze Prediction")+
    scale_color_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    scale_fill_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    theme_classic()+
    theme(plot.title = element_text(size = 20,face="bold",hjust = 0.5),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none"
    )
)

## Exp. 2
(
  plot_fig_3B_exp2<-
    ggplot(data=gz_by_distV_acc_grp_rws%>%dplyr::filter(exp_name=="Exp. 2"),
           aes(x=(dist_v_rule_acc_bin),y=m_gz2pred,color=as.factor(acc),fill=as.factor(acc), group=as.factor(acc)))+
    geom_line(aes(color=as.factor(acc)),alpha=.4,linewidth=2)+
    # geom_point(aes(color=as.factor(acc)))+
    # geom_ribbon(aes(ymin=lo_ci,ymax=hi_ci,fill=as.factor(acc),group=as.factor(acc)), alpha=.2,colour = NA)+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_rule_acc_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    scale_x_continuous(name=" Expectation Strength")+
    scale_y_continuous(name = "Gaze Prediction")+
    scale_color_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    scale_fill_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    # ggtitle("Gaze2Pred diverges  by\n expectation strength & Acc")+
    theme_classic()+
    theme(plot.title = element_text(size = 20,face="bold",hjust = 0.5),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none"
    )
)


# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3B_exp1.pdf"),plot=plot_fig_3B_exp1,width=16,height=16,dpi=600, units="cm",device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3B_exp2.pdf"),plot=plot_fig_3B_exp2,width=16,height=16,dpi=600, units="cm",device = "pdf")

```


### Fig 3C: Benchmark 3 - steeper curve for high Gaze prediction trials

```{r benchmark 3: prep data to look at  of confidence using distV RWS as proxy of evidence}
# binning prediction gz streng
acc_by_gz_distV_RWS_sbs<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  drop_na(dist_v_bin)%>%
  dplyr::group_by(exp_name,sub_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarize(acc=mean(resp_rule_acc),count=n()) 

# summarizing across subject
acc_by_gz_distV_RWS_grp<-acc_by_gz_distV_RWS_sbs%>%
  dplyr::group_by(exp_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarise(lo_ci=CI(acc)[1]*100,hi_ci=CI(acc)[3]*100,m_acc=CI(acc)[2]*100)



```


```{r visualize benchmark 3 for gaze as confidence using V RWS as proxy of evidence, fig.show="hold", out.width="50%" }

#define colors for high/low gaze prediction
cvec_pred_strength<-c("black","azure3")


#Experiment 1
( plot_fig_3C_exp1<-
    ggplot(acc_by_gz_distV_RWS_grp%>%dplyr::filter(exp_name=="Exp. 1"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none"
         )
    )


#Experiment 2
(plot_fig_3C_exp2<-
    ggplot(acc_by_gz_distV_RWS_grp%>%dplyr::filter(exp_name=="Exp. 2"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = c(.9,.2)
         )
)


# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3C_exp1.pdf"),plot=plot_fig_3C_exp1,width=16,height=16,dpi=600, units="cm",device = "pdf")
# ggsave(filename=file.path(path_export_main_pics,"plot_fig_3C_exp2.pdf"),plot=plot_fig_3C_exp2,width=16,height=16,dpi=600, units="cm",device = "pdf")
```

```{r prep data to run prereg stats for Benchmark 3 using lme4  bin only by v5 RWS}
acc_w_gz_distV_RWS_sbs_4stats<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  dplyr::select("exp_name","sub_name","TrialNumber","resp_rule_acc", "pred_gz_bin","dist_v_bin")


```

```{r run prereg stats for Benchmark 3 using lme4  bin only by v5 RWS glmer}
bench3_full_frmla<-resp_rule_acc~pred_gz_bin+dist_v_bin+pred_gz_bin:dist_v_bin+(1|sub_name)

#Exp 1
bench3_full_exp1.res_rws=glmer(bench3_full_frmla,                        
                               data=acc_w_gz_distV_RWS_sbs_4stats%>%filter(exp_name=="Exp. 1")%>%ungroup(),
                               family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")


# Exp 2
bench3_full_exp2.res_rws=glmer(bench3_full_frmla,                        
                               data=acc_w_gz_distV_RWS_sbs_4stats%>%filter(exp_name=="Exp. 2")%>%ungroup(),
                               family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 2")

knitr::kable(bind_rows(bench3_full_exp1.res_rws,bench3_full_exp2.res_rws)%>%dplyr::filter(effect=="fixed"),caption = "Benchmark 3 RWS (glmer)")
```

### Additional analyses on FXP

#### Examine if there is signficant downward slope in the FXP 
Following Rev. 2's request
Here we have an issue of sufficient trials 
We are running with all subjects and also with Ss >= 30 error trials
```{r look if FXPs error slope is sig negative}
# extract df with all ss
RWS_fxp_error_df<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(resp_rule_acc==0)%>%
  dplyr::filter(exp_name%in%c("Exp. 1" ,"Exp. 2"))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::select(sub_name,TrialNumber,resp_rule_acc,dist_v_rule_acc_bin,m_pred_gz,expl.RWS.dist_v_5)%>%
  drop_na(dist_v_rule_acc_bin,resp_rule_acc,m_pred_gz,expl.RWS.dist_v_5)%>%
  dplyr::ungroup()

RWS_fxp_error_df_min_trials<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(resp_rule_acc==0)%>%
  dplyr::filter(exp_name%in%c("Exp. 1" ,"Exp. 2"))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()>29)%>%
  dplyr::select(sub_name,TrialNumber,resp_rule_acc,dist_v_rule_acc_bin,m_pred_gz,expl.RWS.dist_v_5)%>%
  drop_na(dist_v_rule_acc_bin,resp_rule_acc,m_pred_gz,expl.RWS.dist_v_5)%>%
  dplyr::ungroup()

## Running a MM on error  with m_pred_gz~expl.RWS.dist_v_5 as contionous

bench2_negative_trend_full_frmla<-m_pred_gz~expl.RWS.dist_v_5+(1|sub_name)

bench2_negative_trend_full_frmla.RWS=lmer(bench2_negative_trend_full_frmla,
                                          data=RWS_fxp_error_df,
                                          REML = FALSE)

m_null2 <- lmer(m_pred_gz ~ 1 + (1 | sub_name),
               data=RWS_fxp_error_df,
               REML = FALSE)

anova(bench2_negative_trend_full_frmla.RWS, m_null2, test = "Chisq")%>%
  broom::tidy()%>%
  knitr::kable(.,digits =3, caption= "FXP's negative slope m_pred_gz~expl.RWS.dist_v_5 (all subs)")

broom.mixed::tidy(bench2_negative_trend_full_frmla.RWS, effects = "fixed") %>%
  knitr::kable(digits = 3,
               caption = "Fixed effects for the negative trend model (all subs)")

## running with Ss that have n>29

bench2_negative_trend_full_frmla.RWS_m=lmer(bench2_negative_trend_full_frmla,
                                          data=RWS_fxp_error_df_min_trials,
                                          REML = FALSE)

m_null2_m <- lmer(m_pred_gz ~ 1 + (1 | sub_name),
               data=RWS_fxp_error_df_min_trials,
               REML = FALSE)

anova(bench2_negative_trend_full_frmla.RWS_m, m_null2_m, test = "Chisq")%>%
  broom::tidy()%>%
  knitr::kable(.,digits =3, caption= "FXP's negative slope m_pred_gz~expl.RWS.dist_v_5 (min 30 trials)")

broom.mixed::tidy(bench2_negative_trend_full_frmla.RWS_m, effects = "fixed") %>%
  knitr::kable(digits = 3,
               caption = "Fixed effects for the negative trend model (min 30 trials)")

```

### run on FXP's positive slope
```{r look if FXPs correct slope is sig positive}
# extract df with all ss
RWS_fxp_corr_df<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(resp_rule_acc==1)%>%
  dplyr::filter(exp_name%in%c("Exp. 1" ,"Exp. 2"))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::select(sub_name,TrialNumber,resp_rule_acc,dist_v_rule_acc_bin,m_pred_gz,expl.RWS.dist_v_5)%>%
  drop_na(dist_v_rule_acc_bin,resp_rule_acc,m_pred_gz,expl.RWS.dist_v_5)%>%
  dplyr::ungroup()

RWS_fxp_corr_df_min_trials<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(resp_rule_acc==1)%>%
  dplyr::filter(exp_name%in%c("Exp. 1" ,"Exp. 2"))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()>29)%>%
  dplyr::select(sub_name,TrialNumber,resp_rule_acc,dist_v_rule_acc_bin,m_pred_gz,expl.RWS.dist_v_5)%>%
  drop_na(dist_v_rule_acc_bin,resp_rule_acc,m_pred_gz,expl.RWS.dist_v_5)%>%
  dplyr::ungroup()

## Running a MM on error  with m_pred_gz~expl.RWS.dist_v_5 as contionous

bench2_positive_trend_full_frmla<-m_pred_gz~expl.RWS.dist_v_5+(1|sub_name)

bench2_positive_trend_full_frmla.RWS=lmer(bench2_negative_trend_full_frmla,
                                          data=RWS_fxp_corr_df,
                                          REML = FALSE)

m_null2 <- lmer(m_pred_gz ~ 1 + (1 | sub_name),
               data=RWS_fxp_corr_df,
               REML = FALSE)

anova(bench2_positive_trend_full_frmla.RWS, m_null2, test = "Chisq")%>%
  broom::tidy()%>%
  knitr::kable(.,digits =3, caption= "FXP's positive slope m_pred_gz~expl.RWS.dist_v_5 (all subs)")


broom.mixed::tidy(bench2_positive_trend_full_frmla.RWS, effects = "fixed") %>%
  knitr::kable(digits = 3,
               caption = "Fixed effects for the positive trend model (all subs)")

## running with Ss that have n>29

bench2_positive_trend_full_frmla.RWS_m=lmer(bench2_positive_trend_full_frmla,
                                          data=RWS_fxp_corr_df_min_trials,
                                          REML = FALSE)

m_null2_m <- lmer(m_pred_gz ~ 1 + (1 | sub_name),
               data=RWS_fxp_corr_df_min_trials,
               REML = FALSE)

anova(bench2_positive_trend_full_frmla.RWS_m, m_null2_m, test = "Chisq")%>%
  broom::tidy()%>%
  knitr::kable(.,digits =3, caption= "FXP's positive slope m_pred_gz~expl.RWS.dist_v_5 (min 30 trials)")

broom.mixed::tidy(bench2_positive_trend_full_frmla.RWS_m, effects = "fixed") %>%
  knitr::kable(digits = 3,
               caption = "Fixed effects for the positive trend model (min 30 trials)")


```

#### Rev. 2 request to test FXP as a function of trial position within block
Here we are looking at the FXP as a function of early/middle/ late trials within block

so we define as early/mid/late 1-12, 13-22, 23-32
Let's use fixed bins of expectatin strength
```{r prep data to look at FXP by trial pos using fixed values of expectatin strength}

gz_by_distV_RWS_acc_blkpos_df <- mean_gz_prereg_csv %>%
  dplyr::filter(exp_name %in% c("Exp. 1", "Exp. 2")) %>%
  drop_na(expl.RWS.dist_v_5)%>%
  dplyr::mutate(
    trial_pos_blk = if_else(
      rel_trial_number < 12, "Start",
      if_else(rel_trial_number < 23, "Mid", "End")
    ),
    # Bin expectation strength in fixed 0.1 intervals up to 0.5
    expectation_bin = cut(
      expl.RWS.dist_v_5,
      breaks = seq(0, 0.5, by = 0.5/3),
      include.lowest = TRUE,
      # labels = c("0–0.16", "0.16–0.32", "0.32–0.5")
      labels = c("1", "2", "3")
    )
  ) %>%
  dplyr::relocate(c(trial_pos_blk,expl.RWS.dist_v_5,expectation_bin), .after = rel_trial_number) %>%
  dplyr::group_by(sub_name, resp_rule_acc, trial_pos_blk,expectation_bin)%>%
  dplyr::summarize(count=n(),m_gz2pred=mean(m_pred_gz))

gz_by_distV_RWS_acc_blkpos_df$trial_pos_blk<-factor(gz_by_distV_RWS_acc_blkpos_df$trial_pos_blk,levels=c("Start","Mid","End"))
total_trials <- sum(gz_by_distV_RWS_acc_blkpos_df$count)

# summarizing across subjects
smry_gz_by_distV_RWS_acc_blkpos_df<-gz_by_distV_RWS_acc_blkpos_df%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>2)%>%
  
  dplyr::group_by(trial_pos_blk,expectation_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2],n_trials=sum(count),porp_trials=n_trials/total_trials)%>%
  group_by(trial_pos_blk) %>%    # או expectation_bin – לפי מה שאתה רוצה
  mutate(prop_within_blk = n_trials / sum(n_trials))



 
(
ggplot(data = smry_gz_by_distV_RWS_acc_blkpos_df,
       aes(x = expectation_bin,
           y = m_gz2pred,
           color = as.factor(acc),
           fill = as.factor(acc),
           group = as.factor(acc))) +
  geom_line(alpha = .4, linewidth = 2) +
  geom_errorbar(
    aes(ymin = lo_ci, ymax = hi_ci),
    width = 0.1, linewidth = 1, alpha = 0.6
  ) +
  geom_point(aes(size = prop_within_blk), shape = 21, stroke = 1.2) +  # 👈 proportional dot size
  scale_size_continuous(range = c(2, 8), guide = "none") +
  facet_row(~trial_pos_blk) +
  scale_y_continuous(name = "Gaze Prediction") +
    scale_x_discrete(name="Expectation Strength")+
  scale_color_manual(name = "ACC",
                     values = color_vec_benchmark2_acc,
                     labels = c("error", "correct")) +
  scale_fill_manual(name = "ACC",
                    values = color_vec_benchmark2_acc,
                    labels = c("error", "correct")) +
  theme_classic()
)
```

Let's test this statisticaally 

#### Now Running stats on the downward slope of FXP by trial position in block

```{r Running stats on the downward slope of FXP by trial position in block}
# Prep df

df<-mean_gz_prereg_csv %>%
  dplyr::filter(exp_name %in% c("Exp. 1", "Exp. 2")) %>%
  drop_na(expl.RWS.dist_v_5)%>%
  dplyr::mutate(
    trial_pos_blk = if_else(
      rel_trial_number < 12, "Start",
      if_else(rel_trial_number < 23, "Mid", "End")
    ),
    # Bin expectation strength in fixed 0.1 intervals up to 0.5
    expectation_bin = cut(
      expl.RWS.dist_v_5,
      breaks = seq(0, 0.5, by = 0.5/3),
      include.lowest = TRUE,
      # labels = c("0–0.16", "0.16–0.32", "0.32–0.5")
      labels = c("1", "2", "3")
    ),
    acc=as.numeric(resp_rule_acc)
  ) %>%
  dplyr::relocate(c(trial_pos_blk,expl.RWS.dist_v_5,expectation_bin), .after = rel_trial_number)%>%
  dplyr::select(sub_name,TrialNumber,rel_trial_number,trial_pos_blk,acc,expl.RWS.dist_v_5,expectation_bin,m_pred_gz)%>%
  drop_na(expectation_bin,m_pred_gz,acc)%>%
dplyr::mutate(
    acc  = as.numeric(acc),
    expectation_bin = as.numeric(expectation_bin)
  )

# Run Interaction
interaction_by_sub_blk<- df %>%
  group_by(sub_name, trial_pos_blk) %>%
  # dplyr::filter((n_distinct(expectation_bin) == 3 & n_distinct(acc) == 2))%>% #ensure that subject has at least one trial per condition
    dplyr::group_by(sub_name, trial_pos_blk) %>%

  do({
    # Fit model: gaze ~ expectation * accuracy
    fit <- lm(m_pred_gz ~ expectation_bin * acc, data = .)
    # Extract only the interaction term
    broom::tidy(fit) %>%
      # filter(term == "expectation_bin:acc") %>%
      dplyr::select(term, estimate, std.error, statistic, p.value)
  }) %>%
  ungroup()


## run RM Anova on Interaction
res.anova.inter_by_trial_pos<-interaction_by_sub_blk%>%
  dplyr::filter(term == "expectation_bin:acc")%>%
  drop_na(estimate)%>%
anova_test(dv = estimate, wid=sub_name, within=trial_pos_blk)%>%
  get_anova_table()%>%
  as_tibble()%>%
  dplyr::mutate(term="interaction")%>%
  dplyr::relocate(term)%>%
  bind_cols(.,
    interaction_by_sub_blk%>%
  dplyr::filter(term == "expectation_bin:acc")%>%
    dplyr::group_by(trial_pos_blk)%>%
    get_summary_stats(estimate,type="mean_ci")%>%
    dplyr::mutate(lo_ci=mean-ci,hi_ci=mean+ci)%>%
    dplyr::select(trial_pos_blk,mean,lo_ci,hi_ci)%>%
    pivot_wider(
    names_from = trial_pos_blk,
    values_from = c(mean, lo_ci, hi_ci),
    names_glue = "{trial_pos_blk}_{.value}"
  )%>%dplyr::select(
    Start_mean, Start_lo_ci, Start_hi_ci,
    Mid_mean, Mid_lo_ci, Mid_hi_ci,
    End_mean, End_lo_ci, End_hi_ci
  )
)



# Run positive slope
pos_slope_by_sub_trial_pos<- df %>%
  group_by(sub_name, trial_pos_blk) %>%
 dplyr::filter(acc==1)%>%
    dplyr::group_by(sub_name, trial_pos_blk) %>%

  do({
    # Fit model: gaze ~ expectation * accuracy
    fit <- lm(m_pred_gz ~ expectation_bin , data = .)
    # Extract only the interaction term
    broom::tidy(fit) %>%
      # filter(term == "expectation_bin:acc") %>%
      dplyr::select(term, estimate, std.error, statistic, p.value)
  }) %>%
  ungroup()

## run RM Anova on positive slope
res.anova.pos_slope_by_trial_pos<-pos_slope_by_sub_trial_pos%>%
  dplyr::filter(term == "expectation_bin")%>%
  drop_na(estimate)%>%
anova_test(dv = estimate, wid=sub_name, within=trial_pos_blk)%>%
  get_anova_table()%>%
  as_tibble()%>%
  dplyr::mutate(term="positive_slope")%>%
  dplyr::relocate(term)%>%
  bind_cols(.,
    pos_slope_by_sub_trial_pos%>%
  dplyr::filter(term == "expectation_bin")%>%
    dplyr::group_by(trial_pos_blk)%>%
    get_summary_stats(estimate,type="mean_ci")%>%
    dplyr::mutate(lo_ci=mean-ci,hi_ci=mean+ci)%>%
    dplyr::select(trial_pos_blk,mean,lo_ci,hi_ci)%>%
    pivot_wider(
    names_from = trial_pos_blk,
    values_from = c(mean, lo_ci, hi_ci),
    names_glue = "{trial_pos_blk}_{.value}"
  )%>%dplyr::select(
    Start_mean, Start_lo_ci, Start_hi_ci,
    Mid_mean, Mid_lo_ci, Mid_hi_ci,
    End_mean, End_lo_ci, End_hi_ci
  )
)


# Run negative slope
neg_slope_by_sub_trial_pos<- df %>%
  group_by(sub_name, trial_pos_blk) %>%
 dplyr::filter(acc==0)%>%
    dplyr::group_by(sub_name, trial_pos_blk) %>%

  do({
    # Fit model: gaze ~ expectation * accuracy
    fit <- lm(m_pred_gz ~ expectation_bin , data = .)
    # Extract only the interaction term
    broom::tidy(fit) %>%
      dplyr::select(term, estimate, std.error, statistic, p.value)
  }) %>%
  ungroup()

## run RM Anova on positive slope
res.anova.neg_slope_by_trial_pos<-neg_slope_by_sub_trial_pos%>%
  dplyr::filter(term == "expectation_bin")%>%
  drop_na(estimate)%>%
anova_test(dv = estimate, wid=sub_name, within=trial_pos_blk)%>%
  get_anova_table()%>%
  as_tibble()%>%
  dplyr::mutate(term="negative_slope")%>%
  dplyr::relocate(term)%>%
  bind_cols(.,
    neg_slope_by_sub_trial_pos%>%
  dplyr::filter(term == "expectation_bin")%>%
    dplyr::group_by(trial_pos_blk)%>%
    get_summary_stats(estimate,type="mean_ci")%>%
    dplyr::mutate(lo_ci=mean-ci,hi_ci=mean+ci)%>%
    dplyr::select(trial_pos_blk,mean,lo_ci,hi_ci)%>%
    pivot_wider(
    names_from = trial_pos_blk,
    values_from = c(mean, lo_ci, hi_ci),
    names_glue = "{trial_pos_blk}_{.value}"
  )%>%dplyr::select(
    Start_mean, Start_lo_ci, Start_hi_ci,
    Mid_mean, Mid_lo_ci, Mid_hi_ci,
    End_mean, End_lo_ci, End_hi_ci
  )
)

### binding all the  dfs

bind_rows(res.anova.inter_by_trial_pos,res.anova.pos_slope_by_trial_pos)%>%
  bind_rows(.,res.anova.neg_slope_by_trial_pos)%>%
  knitr::kable(.,digits=3, caption="RMANOVA of FXP by trial position in blk")

```

<!-- ```{r run stats on downward FXP by relative position} -->

<!-- bench2_neg_trend_full_frmla<-m_pred_gz~expl.RWS.dist_v_5+(1+expl.RWS.dist_v_5|sub_name) -->
<!-- ## getting for start middle end -->
<!-- FXP_neg_start_down_trend=lmer(bench2_neg_trend_full_frmla, -->
<!--                                           data=gz_by_distV_RWS_acc_trial_pos_df%>% -->
<!--                                             dplyr::filter(trial_pos_blk=="start")%>% -->
<!--                                 dplyr::filter(resp_rule_acc==0), -->
<!--                                           REML = FALSE) -->

<!-- coefs_sub_start <- coef(FXP_neg_start_down_trend)$sub_name %>% -->
<!--   tibble::rownames_to_column("sub_name")%>% -->
<!--   dplyr::mutate(position="start") -->
<!-- #middle -->
<!-- FXP_neg_mid_down_trend=lmer(bench2_neg_trend_full_frmla, -->
<!--                                           data=gz_by_distV_RWS_acc_trial_pos_df%>% -->
<!--                                             dplyr::filter(trial_pos_blk=="mid")%>% -->
<!--                                 dplyr::filter(resp_rule_acc==0), -->
<!--                                           REML = FALSE) -->

<!-- coefs_sub_mid <- coef(FXP_neg_mid_down_trend)$sub_name %>% -->
<!--   tibble::rownames_to_column("sub_name")%>% -->
<!--   dplyr::mutate(position="mid") -->


<!-- #end -->
<!-- FXP_neg_end_down_trend=lmer(bench2_neg_trend_full_frmla, -->
<!--                                           data=gz_by_distV_RWS_acc_trial_pos_df%>% -->
<!--                                             dplyr::filter(trial_pos_blk=="end")%>% -->
<!--                                 dplyr::filter(resp_rule_acc==0), -->
<!--                                           REML = FALSE) -->

<!-- coefs_sub_end <- coef(FXP_neg_end_down_trend)$sub_name %>% -->
<!--   tibble::rownames_to_column("sub_name")%>% -->
<!--   dplyr::mutate(position="end") -->

<!-- all_sub_coeff<-bind_rows(coefs_sub_start,coefs_sub_mid)%>% -->
<!--   bind_rows(.,coefs_sub_end) -->

<!-- all_sub_coeff%>% -->
<!--   dplyr::group_by(position)%>% -->
<!--   get_summary_stats(expl.RWS.dist_v_5) -->

<!-- all_sub_coeff_c<-all_sub_coeff%>% -->
<!--   dplyr::group_by(sub_name)%>% -->
<!--   dplyr::filter(n()==3)%>% -->
<!--   dplyr::ungroup() -->


<!-- anova_test(all_sub_coeff_c,dv = expl.RWS.dist_v_5, wid=sub_name, within=position)%>% -->
<!--   get_anova_table() -->

<!--  all_sub_coeff_c %>% -->
<!--   pairwise_t_test( -->
<!--     expl.RWS.dist_v_5 ~ position, paired = TRUE, -->
<!--     p.adjust.method = "bonferroni" -->
<!--     ) -->

<!-- t_test(data = all_sub_coeff_c%>%dplyr::filter(position!="start")%>%arrange(sub_name),formula = expl.RWS.dist_v_5~position,paired = T ) -->

<!-- ( -->
<!--   ggplot(data=all_sub_coeff_c,aes(x=position, y=expl.RWS.dist_v_5))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_point() -->
<!-- ) -->
<!-- ``` -->





### Table S5 & S6 PWC of benchmarks

Table S5
```{r get statistic tables of benchmark 2 pairwise comparisons RWS}
#getting summary
smry_vals_gz_by_distV_RWS_acc_pairwise<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  # dplyr::group_by(sub_name)%>%
  # dplyr::filter(n()!=12)%>%
  dplyr::group_by(exp_name,dist_v_rule_acc_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2])%>%
  pivot_wider(names_from = acc, values_from = c(lo_ci,hi_ci,m_gz2pred))

#get stats
stats_gz_by_distV_RWS_acc_pairwise<-gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>4)%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin)%>%
  dplyr::filter(n()==2 )%>% #removing Ss with less than 5 items per bin
  dplyr::group_by(exp_name,dist_v_rule_acc_bin)%>%
  
  dplyr::summarise(p_val=t.test(m_gz2pred~acc,paired = TRUE)$p.value,
                   t=t.test(m_gz2pred~acc,paired = TRUE)$statistic,
                   df=t.test(m_gz2pred~acc,paired = TRUE)$parameter)

#joining
smry_gz_by_distV_RWS_acc_pairwise<-full_join(smry_vals_gz_by_distV_RWS_acc_pairwise,
                                             stats_gz_by_distV_RWS_acc_pairwise,
                                             by=c("exp_name","dist_v_rule_acc_bin")
                                             
)

knitr::kable(smry_gz_by_distV_RWS_acc_pairwise,digits=4,caption="SM table B2 pairise comparison of Benchmark 2 RWS")

```

```{r run pairwise comparison of Bench 2 RWS }
sbs_bench2_RWS<-gz_by_distV_RWS_acc_df%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  # dplyr::filter(count>4)%>% # Currently not filtering out subjects except those without any values in bin
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==12)

pwc_bench_2_RWS <- sbs_bench2_RWS %>% 
  ungroup()%>%
  group_by(dist_v_rule_acc_bin) %>%
  pairwise_t_test(
    m_gz2pred ~ acc, paired = TRUE,
    p.adjust.method = "bonferroni"
    )%>%dplyr::select(dist_v_rule_acc_bin,statistic,df,p,p.adj)%>%
  dplyr::mutate(model="sRW")


```


#### Table S6 PWC of benchmark 3

```{r pairwise comparison of Bench 3 RWS}
sbs_bench3_RWS<-acc_w_gz_distV_RWS_sbs_4stats%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,pred_gz_bin,dist_v_bin)%>%
  dplyr::summarise(m_acc=mean(resp_rule_acc)*100,count=n())%>%
  # dplyr::filter(count>4)%>% # Currently not filtering out subjects except those without any values in bin
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==12)

pwc_bench_3_RWS <- sbs_bench3_RWS %>% 
  ungroup()%>%
  group_by(dist_v_bin) %>%
  pairwise_t_test(
    m_acc ~ pred_gz_bin, paired = TRUE,
    p.adjust.method = "bonferroni"
    )%>%
  dplyr::select(dist_v_bin,statistic,df,p,p.adj)%>%
  dplyr::mutate(model="RWS")
```



### Fig. S7 Confidence Hallmarks using RW RW
```{r benchmark 3: prep data to look at  of confidence using distV RW as proxy of evidence}


# binning prediction gz streng
acc_by_gz_distV_RW_sbs<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RW.dist_v_5,6))%>% #binning  distance of V
  dplyr::filter(!is.na(dist_v_bin))%>%
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RW.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  dplyr::group_by(exp_name,sub_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarize(acc=mean(resp_rule_acc),count=n()) 




# summarizing across subject
acc_by_gz_distV_RW_grp<-acc_by_gz_distV_RW_sbs%>%
  dplyr::group_by(exp_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarise(lo_ci=CI(acc)[1]*100,hi_ci=CI(acc)[3]*100,m_acc=CI(acc)[2]*100)



```

#### Fig S7 Right
```{r visualize benchmark 3 for gaze as confidence using V RW as proxy of evidence, fig.show="hold", out.width="50%" }

#define colors for high/low gaze prediction
cvec_pred_strength<-c("black","azure3")


#Experiment 1
(plot_SM_fig_S5_c_exp1<-
    ggplot(acc_by_gz_distV_RW_grp%>%dplyr::filter(exp_name=="Exp. 1"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none"
         )
    )


#Experiment 2
(plot_SM_fig_S5_c_exp2<-
    ggplot(acc_by_gz_distV_RW_grp%>%dplyr::filter(exp_name=="Exp. 2"),
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = c(.9,.2)
         )
)

# ##saving
# #exp1
# ggsave(filename=file.path(path_export_sm_pics,"plot_SM_fig_S5_c_exp1.png"),plot=plot_SM_fig_S5_c_exp1,dpi=600, units="cm",device = "png")
# # exp.2 
# ggsave(filename=file.path(path_export_sm_pics,"plot_SM_fig_S5_c_exp2.png"),plot=plot_SM_fig_S5_c_exp2,dpi=600, units="cm",device = "png")
```


```{r prep data to run prereg stats for Benchmark 3 using lme4  bin only by v5 RW}
acc_w_gz_distV_RW_sbs_4stats<-mean_gz_prereg_csv%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RW.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RW.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  dplyr::select("exp_name","sub_name","TrialNumber","resp_rule_acc", "pred_gz_bin","dist_v_bin")


```

```{r run prereg stats for Benchmark 3 using lme4  bin only by v5 RW glmer}
bench3_full_frmla<-resp_rule_acc~pred_gz_bin+dist_v_bin+pred_gz_bin:dist_v_bin+(1|sub_name)

#Exp 1
bench3_full_exp1.res=glmer(bench3_full_frmla,                        
                           data=acc_w_gz_distV_RW_sbs_4stats%>%filter(exp_name=="Exp. 1")%>%ungroup(),
                           family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")


# Exp 2
bench3_full_exp2.res=glmer(bench3_full_frmla,                        
                           data=acc_w_gz_distV_RW_sbs_4stats%>%filter(exp_name=="Exp. 2")%>%ungroup(),
                           family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 2")

knitr::kable(bind_rows(bench3_full_exp1.res,bench3_full_exp2.res)%>%dplyr::filter(effect=="fixed"),caption = "Benchmark 3 (glmer)")
```


```{r pairwise comparison of Bench 3 RW}
sbs_bench3_RW<-acc_w_gz_distV_RW_sbs_4stats%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,pred_gz_bin,dist_v_bin)%>%
  dplyr::summarise(m_acc=mean(resp_rule_acc)*100,count=n())%>%
  # dplyr::filter(count>4)%>% # Currently not filtering out subjects except those without any values in bin
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==12)

pwc_bench_3_RW <- sbs_bench3_RW %>% 
  ungroup()%>%
  group_by(dist_v_bin) %>%
  pairwise_t_test(
    m_acc ~ pred_gz_bin, paired = TRUE,
    p.adjust.method = "bonferroni"
    )%>%
  dplyr::select(dist_v_bin,statistic,df,p,p.adj)%>%
  dplyr::mutate(model="RW")
```



## Fig 4

First let's examine the relation between explicit cnfidence and P. Choice

### Correlation of Confidence and RWS trial-by-trial trajectories

```{r prep data to look at correltaion between RW traj & confidence ratings}

corr_RWS_conf_ps<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  dplyr::summarize(r.conf_PC=rcorr(z_conf_rating,expl.RWS.p_choice)$r[2],pval.conf_PC=rcorr(z_conf_rating,expl.RWS.p_choice)$P[2],
                   r.conf_prev_delta=rcorr(z_conf_rating,expl.RWS.prev_delta)$r[2],pval.conf_prev_delta=rcorr(z_conf_rating,expl.RWS.prev_delta)$P[2],
                    r.conf_dist_v=rcorr(z_conf_rating,expl.RWS.dist_v_5)$r[2],pval.conf_dist_v=rcorr(z_conf_rating,expl.RWS.dist_v_5)$P[2]
  )



#doing for pval
p_val_long<-corr_RWS_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("pval")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


sum_p_val=p_val_long%>%
  group_by(vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig),total_sub=n())


# doing for corr
corr_val_long<-corr_RWS_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("r")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")




sum_corr_conf_rating_rw_traj<-corr_val_long%>%
  group_by(vars_compared)%>%
  dplyr::summarise(mean_corr=CI(val)[2],hi_CI=CI(val)[1],lo_CI=CI(val)[3],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                   ES=one_sample_ttest_cohen_d(val)
                   )%>%
  full_join(.,sum_p_val,by="vars_compared")

knitr::kable(sum_corr_conf_rating_rw_traj%>% 
               dplyr::filter(vars_compared!="conf_dist_v"),
             digits = 3, caption = "correlation Confidence Ratings  and sRW trajectories")


```

So there is a super robust correlation between P. Choice and confidence ratings 30/32 Ss are significant!

### Figure 4A

Correlation of confidence & Gaze
```{r prep data to lookk at relation of conf rating  and EM}

# running the correlation analysis
corr_gz_conf_ps<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  dplyr::summarize(r.conf_gz2pred=rcorr(z_conf_rating,m_pred_gz)$r[2],pval.conf_gz2pred=rcorr(z_conf_rating,m_pred_gz)$P[2]
  )

#doing for pval
p_val_corr_gz_conf_ps_long<-corr_gz_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("pval")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


# doing for corr
corr_val_corr_gz_conf_ps_long<-corr_gz_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("r")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")


##all subjects
sum_p_val_corr_gz_conf_ps=p_val_corr_gz_conf_ps_long%>%
  group_by(vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig),total_sub=n())


sum_corr_gz_conf<-corr_val_corr_gz_conf_ps_long%>%
  group_by(vars_compared)%>%
  dplyr::summarise(mean_corr=CI(val)[2],lo_corr=CI(val)[3],hi_corr=CI(val)[1],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                   ES=one_sample_ttest_cohen_d(val))%>%
  full_join(.,sum_p_val_corr_gz_conf_ps,by="vars_compared")

knitr::kable(sum_corr_gz_conf,digits = 4, caption = "Experiment 3 correlation Confidence Ratings  and EM")


```

```{r viz correlation values of of conf rating  and EM}
#all subjects
corr_conf_gz2pred<-corr_val_corr_gz_conf_ps_long%>%
  dplyr::filter(vars_compared=="conf_gz2pred")%>%
  dplyr::filter(value_type=="corr")

grp_corr_conf_gz2pred<-corr_conf_gz2pred%>%
  dplyr::ungroup()%>%
  dplyr::summarize(grp_mean=CI(val)[2],lo_ci=CI(val)[1],hi_ci=CI(val)[3])



(
  plot_fig_4A<-
    ggplot(data=corr_conf_gz2pred,aes(y=val,x=1))+
            xlim(c(.5,1.5))+
    ylim(c(-.1,.3))+

       geom_boxplot(outlier.shape = NA,linewidth=1,color="black",size=.5,width=.4)+ #,width=.02
    # geom_pointrange (data=grp_corr_pc_gz2pred_rws%>%dplyr::filter(exp_name!="Exp. 3"), aes(y=grp_mean,ymin=lo_ci, ymax=hi_ci),size=3,fatten=1.5,width=.1, color="black")+
    

    geom_point(color="#707070",position = position_jitter(width=.1),size=3, alpha = .8)+
    
    # geom_hline(yintercept = 0, color="red",linetype="solid",size=1.5)+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
ylab(expression(atop(rho, "\n Gaze & Confidence")))+

    theme_classic()+
    # coord_fixed(ratio = 4,xlim = c(0.8, 1.2))+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          strip.background = element_blank(),
          legend.position = "none"
    )
)

 

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_4A_240624.pdf"),plot=plot_fig_4A,width=16,height=16,dpi=600, units="cm",device = "pdf")
```


### Control analysis of Relation between Confidence and Gaze Prediction beyond p. choice


Running a mixed model examining relation between Gaze, confidence & other factors

So confidence & gaze are correlated but we also know that there are both correlated with a bunch of other factors (most notably P. Choice, accuracy). 
So using mixed models lets try to tease apart these factors



```{r mixed model analysis of gaze and confidence control p choice} 
#Test with if Gaze pred
##P.Choice

#full model
conf_gz_pchoice_mdl<-z_conf_rating~m_pred_gz+expl.RWS.p_choice+(1|sub_name)
# conf_gz_pchoice_mdl<-z_conf_rating ~ m_pred_gz + expl.RWS.p_choice + 
#                 (1 + m_pred_gz + expl.RWS.p_choice | sub_name)


gz_conf_mdl2_full.res=lmer(conf_gz_pchoice_mdl,data=mean_gz_prereg_exp3,REML = FALSE)

# remove Confidence
conf_gz_pchoice_mdl_no_gz<-conf_gz_pchoice_mdl<-z_conf_rating ~  expl.RWS.p_choice + 
                (1 | sub_name)

# conf_gz_pchoice_mdl_no_gz<-conf_gz_pchoice_mdl<-z_conf_rating ~  expl.RWS.p_choice + 
#                 (1 +  expl.RWS.p_choice | sub_name)

conf_gz_pchoice_mdl_no_gz.res=lmer(conf_gz_pchoice_mdl_no_gz,data=mean_gz_prereg_exp3,REML = FALSE)

#test with anova

conf_by_gz_PC_aov_res<-anova(gz_conf_mdl2_full.res,conf_gz_pchoice_mdl_no_gz.res)%>%
  tidy()%>%
  dplyr::filter(!is.na(df))

knitr::kable(conf_by_gz_PC_aov_res,digits=4, caption="MM results of gaze by confidence & P. Choice")
# 
# # Install if necessary: install.packages("effectsize")
# library(effectsize)
# conf_by_gz_PC_aov_res_raw<-anova(gz_conf_mdl2_full.res,conf_gz_pchoice_mdl_no_gz.res)
# raw_aov_comparison <- anova(conf_gz_pchoice_mdl_no_gz.res, gz_conf_mdl2_full.res)
# # Calculate effect size for the model comparison
# comparison_es <- effectsize(conf_by_gz_PC_aov_res_raw)
# 
# print(comparison_es)
```

getting effect size of gaze
```{r testing the Effect size of adding in gaze to examinerelation to Confidnce}
library(performance)
# Get R2 for both models
r2_full <- r2(gz_conf_mdl2_full.res)
r2_red  <- r2(conf_gz_pchoice_mdl_no_gz.res)

# Calculate the difference
delta_r2 <- r2_full$R2_marginal - r2_red$R2_marginal

# View results
res_table <- data.frame(
  Model = c("Reduced", "Full", "Difference"),
  Marginal_R2 = c(r2_red$R2_marginal, r2_full$R2_marginal, delta_r2)
)

knitr::kable(res_table, digits = 4, caption = "Variance explained (R2) by adding Gaze Prediction")

r2_f <- r2(gz_conf_mdl2_full.res)$R2_marginal
r2_r <- r2(conf_gz_pchoice_mdl_no_gz.res)$R2_marginal

f2 <- (r2_f - r2_r) / (1 - r2_f)
cat("Cohen's f2 for the addition of gaze prediction is:", round(f2, 4))
```






#### Trying a group summary approach.
We fit for each subject individually while controlling for additional factors and then do a group ttest


```{r grpsummary approach of conf by gz and other factors}
# 1. Calculate regression slopes per subject
slopes <- mean_gz_prereg_exp3 %>%
  dplyr::group_by(sub_name) %>%
  dplyr::reframe(
    # Fit linear model for each subject
    fit = list(lm(z_conf_rating ~ m_pred_gz + expl.RWS.p_choice, 
                  data = dplyr::pick(dplyr::everything()))),
    # Extract coefficients
    beta_m_pred_gz = coef(fit[[1]])["m_pred_gz"],
    beta_explRWS = coef(fit[[1]])["expl.RWS.p_choice"]
  ) %>%
  dplyr::select(-fit) %>%
  tidyr::pivot_longer(!sub_name, names_to = "predictor", values_to = "val") %>%
  # Crucial: Force numeric type and remove NAs for rstatix functions
  dplyr::mutate(val = as.numeric(val)) %>%
  dplyr::filter(!is.na(val))

# 2. Join t-test, Cohen's d, and Summary Stats
final_analysis <- dplyr::left_join(
  slopes %>%
    dplyr::group_by(predictor) %>%
    rstatix::t_test(val ~ 1, mu = 0) %>%
    dplyr::select(predictor, statistic, df, p),
  
  slopes %>%
    dplyr::group_by(predictor) %>%
    rstatix::cohens_d(val ~ 1, mu = 0) %>%
    dplyr::select(predictor, effsize),
  by = "predictor"
) %>%
  dplyr::left_join(
    slopes %>%
      dplyr::group_by(predictor) %>%
      rstatix::get_summary_stats(val, type = "mean_ci"),
    by = "predictor"
  )

# 3. Output the final styled table
final_analysis %>%
  knitr::kable(digits = 3, 
               caption = "Gaze Prediction correlated to confidence beyond p choice")
```


Looking at additional factors: m_pred_gz~z_conf_rating+expl.RWS.p_choice+resp_rule_acc+expl.RWS.prev_delta+(1|sub_name)


```{r Prep data for  mixed model analysis of gaze and confidence}
#Test with if Gaze pred
##P.Choice


#full model
gz_dv_mdl2_full<-m_pred_gz~z_conf_rating+expl.RWS.p_choice+resp_rule_acc+expl.RWS.prev_delta+(1|sub_name)
gz_conf_mdl2_full.res=lmer(gz_dv_mdl2_full,data=mean_gz_prereg_exp3,REML = FALSE)

# remove Confidence
gz_dv_mdl2_no_conf<-m_pred_gz~expl.RWS.p_choice+resp_rule_acc+expl.RWS.prev_delta+(1|sub_name)
gz_dv_mdl2_no_conf.res=lmer(gz_dv_mdl2_no_conf,data=mean_gz_prereg_exp3,REML = FALSE)

#test with anova

gz_by_conf_PC_aov_res<-anova(gz_conf_mdl2_full.res,gz_dv_mdl2_no_conf.res)%>%
  tidy()%>%
  dplyr::filter(!is.na(df))

knitr::kable(gz_by_conf_PC_aov_res,digits=4, caption="MM results of gaze by confidence & other variables")
```


#### looking at the inverse relation with Gaze Prediction as DV

```{r ruuning with gaze prediction as the DV}
# 1. Calculate slopes per subject and clean output
slopes <- mean_gz_prereg_exp3 %>%
  dplyr::group_by(sub_name) %>%
  dplyr::reframe(
    # Using reframe + list() to safely run lm within the pipe
    fit = list(lm(m_pred_gz ~ z_conf_rating + expl.RWS.p_choice + resp_rule_acc + expl.RWS.prev_delta, 
                  data = dplyr::pick(dplyr::everything()))),
    beta_z_conf_rating = coef(fit[[1]])["z_conf_rating"],
    beta_explRWS = coef(fit[[1]])["expl.RWS.p_choice"],
    beta_resp_rule_acc = coef(fit[[1]])["resp_rule_acc"],
    beta_prev_delta = coef(fit[[1]])["expl.RWS.prev_delta"]
  ) %>%
  dplyr::select(-fit) %>%
  tidyr::pivot_longer(!sub_name, names_to = "predictor", values_to = "val") %>%
  # Fix: Force numeric type and remove NAs that break cohens_d
  dplyr::mutate(val = as.numeric(val)) %>%
  dplyr::filter(!is.na(val))

# 2. Compute group-level statistics
results_table <- dplyr::left_join(
  slopes %>%
    dplyr::group_by(predictor) %>%
    rstatix::t_test(val ~ 1, mu = 0) %>%
    dplyr::select(predictor, statistic, df, p),
  
  slopes %>%
    dplyr::group_by(predictor) %>%
    rstatix::cohens_d(val ~ 1, mu = 0) %>%
    dplyr::select(predictor, effsize),
  by = "predictor"
) %>%
  dplyr::left_join(
    slopes %>%
      dplyr::group_by(predictor) %>%
      rstatix::get_summary_stats(val, type = "mean_ci"),
    by = "predictor"
  )

# 3. Render the final table
results_table %>%
  knitr::kable(digits = 3, 
               caption = "Gaze Prediction correlated to confidence beyond other factors")
```

### Fig 4 B

Comparing metacognition of eye vs. explicit ratings confidence.

```{r prep data to compare metacognition eye vs rating}
rating_eye_delta_conf<-mean_gz_prereg_exp3%>%
  group_by(sub_name,resp_rule_acc)%>%
  dplyr::summarize(m_conf_rating=mean(conf_rating),m_eye_rating=mean(gz_conf))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(diff_rating_expl=m_conf_rating-first(m_conf_rating),
                diff_rating_eye=m_eye_rating-first(m_eye_rating))%>%
  dplyr::filter(diff_rating_expl!=0)

rating_eye_delta_conf_long<-rating_eye_delta_conf%>%
  dplyr::select(sub_name,diff_rating_expl,diff_rating_eye)%>%
  pivot_longer(cols = starts_with("diff"),names_prefix = "diff_rating_", names_to = "source",values_to = "diff_value")

```


```{r visualize Fig 4B metacognition of eye vs explicit rating}

(plot_fig_4B<-
    ggpaired(data=rating_eye_delta_conf_long,
             x="source",y="diff_value",id="sub_name",fill="source",line.color = "lightgrey",alpha=.1,line.size = .2)+
    # scale_y_continuous(name="Delta confidence")+
    scale_y_continuous(expression(Delta ~ "Confidence"))+
    scale_x_discrete(name="Confidence Source",labels=c("Explicit","Gaze"))+
    scale_fill_manual(values = color_vec_eye_expl_source)+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none"
    )
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_4B.pdf"),plot=plot_fig_4B,width=16,height=16,dpi=600, units="cm",device = "pdf")

```

So we see a big win for Explicit Rating! They have much higher metacognition


```{r stats for comparison of explicit and eye delat confidence}

stats_expl_eye_delta_conf<-bind_cols(
  t.test(data=rating_eye_delta_conf_long, diff_value~source, paired=TRUE)%>%
    tidy()%>%
    dplyr::select(estimate, conf.low,conf.high,statistic,p.value,parameter),
  
  rstatix::cohens_d(data=rating_eye_delta_conf_long%>%ungroup(), diff_value~source, paired=TRUE)%>%dplyr::select(effsize)
)

knitr::kable(stats_expl_eye_delta_conf,digits=3,caption= "ttest results of delta confidence expl vs. eye")

```

#### stats of each measures metacognitive sensitivity 
i.e. delta confidence >0

```{r run stats to see if eye_expl have delta confidence greater than zero}
grp_delta_conf_by_source<-rating_eye_delta_conf_long%>%
  dplyr::group_by(source)%>%
  dplyr::summarise(mean=CI(diff_value)[2],lo_ci=CI(diff_value)[3],hi_ci=CI(diff_value)[1],
                   statistic=t.test(diff_value)$statistic,
                   p_val=t.test(diff_value)$p.value,
                   ES=one_sample_ttest_cohen_d(diff_value))

knitr::kable(grp_delta_conf_by_source,digits =3, caption = "explicit/eye confidence one sample ttest")


```


### Fig S9: correlation between Explicit and Ocular metacognition

Examine the correlation between Explicit and Ocular metacognitionacross SS

```{r get stats for corr of eye & explicit rating delta confidence }

#get Bayes Factor (BF) for correlation of delta confidence of eyes & ratings
BF_corr_rating_eye_delta_conf<-correlationBF(rating_eye_delta_conf$diff_rating_expl,rating_eye_delta_conf$diff_rating_eye)%>%
  bayesfactor_models()

#transforming from log 
BF_corr_rating_eye_delta_conf<-exp(1)^BF_corr_rating_eye_delta_conf$log_BF[2]
#push into df
expl_eye_metacog_exp3_corr_stats<-tibble(
  r=rcorr(rating_eye_delta_conf$diff_rating_expl,rating_eye_delta_conf$diff_rating_eye)$r[2],
  pval =rcorr(rating_eye_delta_conf$diff_rating_expl,rating_eye_delta_conf$diff_rating_eye)$P[2],
  df=nrow(rating_eye_delta_conf)-1,
  BF=BF_corr_rating_eye_delta_conf)

knitr::kable(expl_eye_metacog_exp3_corr_stats, digits=2,caption = "stats of correlation between explicit and ocular metacognition")

```


```{r viz Fig S8 correlate eye & explicit rating difference}


(plot_SM_fig_S8<-
  ggplot(data=rating_eye_delta_conf,aes(x=diff_rating_expl,y=diff_rating_eye))+
    geom_point()+
    geom_smooth(method=lm)+

    xlab(" Explicit \u0394 confidence")+
    ylab("Ocular \u0394 confidence")+
    theme_bw()+
    theme(title = element_text(size = 16,face="bold"),
          plot.subtitle=  element_text(size = 14,angle=0),
          
          axis.title.x = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none") 
)

# ggsave(plot = plot_SM_fig_S8,filename = file.path(path_export_sm_pics,"SM_fig_S8_corr_ocular_explicit_metacog.jpg"), units = "cm")

```

This is interesting! Eye metacognition & Explict Metacognition seem to be somewhat unrelated abilities.

BF is inconclusive

Need to check this with Bayesian null analysis and sample size is still small so prbly think of a way to show at a trial level that the two diverge

##### further test for correlation between metacognition across SS
So let's try also controling for each Ss's rule acc
```{r test corr between Ss metacognition and rule acc}

rating_eye_delta_conf_w_acc<-full_join(rating_eye_delta_conf,
                                       mean_gz_prereg_exp3%>%
                                         dplyr::group_by(sub_name)%>%
                                         dplyr::summarise(m_acc=mean(resp_rule_acc)),
                                       by="sub_name")

f<-lm(diff_rating_expl~diff_rating_eye*m_acc,data = rating_eye_delta_conf_w_acc)

knitr::kable(summary(f)%>%tidy(), digits=3, caption="expl. meta by eye meta: rule acc")
```


### Fig 4C: serial dependence of explicit and ocular confidence
looking at difference in Serial Dependence in Exp 3 between explicit and ocular confidence rating

Start by simply looking at lag 1 autocorrelation between the two types of confidence

```{r prep data compare simple lag1 autocorrelation of gaze and explicit cofidence exp 3}
#exp 3
conf_by_prev_trial_exp3_tbt<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(prev_gz_conf=lag(z_gz_conf),
                prev_expl_conf=lag(z_conf_rating))%>%
  dplyr::relocate(prev_gz_conf,.after=z_gz_conf)%>%
  dplyr::relocate(prev_expl_conf,.after=z_conf_rating)%>%
  dplyr::filter(is_trial_consec==1)%>%
  dplyr::filter(!is.na(prev_gz_conf))%>%
  dplyr::filter(!is.na(z_gz_conf))%>%
  dplyr::filter(!is.na(z_conf_rating))%>%
  dplyr::filter(!is.na(prev_expl_conf))

#prep data
# get explicit confidence ratings autocorrealtion
expl_conf_autocorrelation <- conf_by_prev_trial_exp3_tbt %>%
  group_by(sub_name) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lm(z_conf_rating ~ prev_expl_conf, data = .x)),
    results = map(model, tidy)
  ) %>%
  unnest(results)%>%
  dplyr::filter(term=="prev_expl_conf")%>%
  dplyr::select(sub_name,estimate)%>%
  dplyr::rename("conf_ac_expl"=estimate)


gz_conf_autocorrelation <- conf_by_prev_trial_exp3_tbt %>%
  group_by(sub_name) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lm(z_gz_conf ~ prev_gz_conf, data = .x)),
    results = map(model, tidy)
  ) %>%
  unnest(results)%>%
  dplyr::filter(term=="prev_gz_conf")%>%
  dplyr::select(sub_name,estimate)%>%
  dplyr::rename("conf_ac_gz"=estimate)

## joining
conf_auto_corr_df<-inner_join(expl_conf_autocorrelation,gz_conf_autocorrelation,
                              by="sub_name")%>%
  dplyr::ungroup()%>%
  pivot_longer(cols = !sub_name,names_prefix = "conf_ac_", names_to = "source",values_to = "auto_corr_val")

```

```{r  stats simple autocorrelation of gaze and explicit cofidence}
#print stats of paired t-test
bind_cols(
  t_test(data=conf_auto_corr_df,auto_corr_val~source, paired = T)%>%
    dplyr::select(-".y."),
rstatix::cohens_d(data=conf_auto_corr_df,auto_corr_val~source, paired = T)%>%
    dplyr::select(effsize)
)%>%
  knitr::kable(.,caption="Comparison of Lag1 Autocorrelation of explicit & ocular conf. Exp 3",digit=3)
```

```{r plot fig 4C lag 1 autocorrelation}
color_vec_eye_expl_source=c("burlywood2", "paleturquoise2")

#plot acc on cong vs. incong
(plot_fig_4C<-ggpaired(data =conf_auto_corr_df,
          x="source", y="auto_corr_val", id="sub_name",fill = "source",line.color = "lightgrey",alpha=.1,line.size = .2 )+
    scale_x_discrete(name= "Source",labels=c("Explicit","Gaze"))+
    scale_fill_manual(values = color_vec_eye_expl_source)+
    scale_y_continuous(name= "Lag 1 Autocorrelation ")+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          legend.position = "none") 
  
)

# ggsave(filename=file.path(path_export_main_pics,"plot_fig_4C_autocorr.pdf"),plot=plot_fig_4C,width=16,height=16,dpi=600, units="cm",device = "pdf")

```
### One-sample ttest of explicit & ocular confidence in exp 3
Is there a significant effect of serial dependence for each type of source
Let's check if each type of confidence's autocorrealtion of gaze is sig. diff than zero

```{r run stats on one sample ttest of explicit and ocular sd exp 3 }

#summary stats of Exp. 3 serial dependence effects by source
conf_auto_corr_df%>%
  dplyr::group_by(source)%>%
  dplyr::summarise(mean_auto_corr_val=CI(auto_corr_val)[2],lo_ci=CI(auto_corr_val)[3],hi_ci=CI(auto_corr_val)[1])%>%
  knitr::kable(.,caption = "Summary stats of auto correlation values Exp. 3",digits = 3)

  

bind_cols(conf_auto_corr_df%>%
  dplyr::group_by(source)%>%
  t_test(auto_corr_val~1),
  conf_auto_corr_df%>%
  dplyr::group_by(source)%>%
  rstatix::cohens_d(auto_corr_val~1)%>%
    dplyr::select(effsize)
) %>%
  # dplyr::select(source,statistic,p)%>%
  knitr::kable(.,caption = "one sample t-test of distribution of auto correlation values Exp. 3",digits = 3)



```


So we see that lag1 autocorr in exp 3 is sig. for explicit but not for ocular

Let's look at autocorrelation of gaze in exp 1&2
### One-sample ttest of  ocular confidence across experiments 1& 2

```{r prep data compare simple autocorrelation of gaze cofidence ratings exp 1& 2}
#exp 3
gz_conf_by_prev_trial_tbt_exp12<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(prev_gz_conf=lag(z_gz_conf))%>%
  dplyr::relocate(prev_gz_conf,.after=z_gz_conf)%>%
  dplyr::filter(is_trial_consec==1)%>%
  dplyr::filter(!is.na(prev_gz_conf))%>%
  dplyr::filter(!is.na(z_gz_conf))

#prep data
# get Ocular confidence ratings autocorrealtion
gz_conf_autocorrelation_exp12 <-gz_conf_by_prev_trial_tbt_exp12 %>%
  group_by(exp_name,sub_name) %>%
  nest() %>%
 mutate(
    model = map(data, ~ lm(z_gz_conf ~ prev_gz_conf, data = .x)),
    results = map(model, tidy)
  ) %>%
  unnest(results)%>%
  dplyr::filter(term=="prev_gz_conf")%>%
  dplyr::select(exp_name,sub_name,estimate)%>%
  dplyr::rename("auto_corr_val"=estimate)

gz_conf_autocorrelation_exp12 <-gz_conf_autocorrelation_exp12 %>%
  dplyr::ungroup()
```


```{r run stats on one sample ttest of explicit and ocular sd exp12 }

#summary stats of Exp. 3 serial dependence effects by source
gz_conf_autocorrelation_exp12%>%
  dplyr::summarise(mean_auto_corr_val=CI(auto_corr_val)[2],lo_ci=CI(auto_corr_val)[3],hi_ci=CI(auto_corr_val)[1])%>%
  knitr::kable(.,caption = "Summary stats of ocular auto correlation values Exp. 1&2",digits = 3)

  

bind_cols(gz_conf_autocorrelation_exp12%>%
  t_test(auto_corr_val~1)%>%
    dplyr::select(n:p),
  gz_conf_autocorrelation_exp12%>%
  rstatix::cohens_d(auto_corr_val~1)%>%
    dplyr::select(effsize)
) %>%
  # dplyr::select(source,statistic,p)%>%
  knitr::kable(.,caption = "one sample t-test of distribution of auto correlation values Exp. 1 & 2",digits = 3)



```

#### SM analysis: test that autocorrelation is not driven by additional factors

Here we are looking at autcorreation but controling for p. choice and prev. trial's accuracy

```{r compare more controlled autocorrelation of gaze and explicit cofidence}
# conf_by_prev_trial_exp3_tbt<-mean_gz_prereg_df%>%
#   dplyr::filter(exp_name%in%c("Exp. 3"))%>%
#   dplyr::group_by(sub_name)%>%
#   dplyr::mutate(prev_gz_conf=lag(z_gz_conf),
#                 prev_expl_conf=lag(z_conf_rating))%>%
#   dplyr::relocate(prev_gz_conf,.after=z_gz_conf)%>%
#   dplyr::relocate(prev_expl_conf,.after=z_conf_rating)%>%
#   dplyr::filter(is_trial_consec==1)%>%
#   dplyr::filter(!is.na(prev_gz_conf))%>%
#   dplyr::filter(!is.na(z_gz_conf))%>%
#   dplyr::filter(!is.na(z_conf_rating))%>%
#   dplyr::filter(!is.na(prev_expl_conf))

#prep data
# get explicit confidence ratings autocorrealtion
expl_conf_autocorrelation_full <- conf_by_prev_trial_exp3_tbt %>%
  group_by(sub_name) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lm(z_conf_rating ~ prev_expl_conf+prev_acc+expl.RWS.p_choice, data = .x)),
    results = map(model, tidy)
  ) %>%
  unnest(results)%>%
  dplyr::filter(term=="prev_expl_conf")%>%
  dplyr::select(sub_name,estimate)%>%
  dplyr::rename("conf_ac_expl"=estimate)


gz_conf_autocorrelation_full <- conf_by_prev_trial_exp3_tbt %>%
  group_by(sub_name) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lm(z_gz_conf ~ prev_gz_conf+prev_acc+expl.RWS.p_choice, data = .x)),
    results = map(model, tidy)
  ) %>%
  unnest(results)%>%
  dplyr::filter(term=="prev_gz_conf")%>%
  dplyr::select(sub_name,estimate)%>%
  dplyr::rename("conf_ac_gz"=estimate)

conf_auto_corr_full_df<-inner_join(expl_conf_autocorrelation_full,gz_conf_autocorrelation_full,
                              by="sub_name")%>%
  dplyr::ungroup()%>%
  pivot_longer(cols = !sub_name,names_prefix = "conf_ac_", names_to = "source",values_to = "auto_corr_val")

bind_cols(
t_test(data=conf_auto_corr_full_df,auto_corr_val~source, paired = T),
rstatix::cohens_d(data=conf_auto_corr_full_df,auto_corr_val~source, paired = T)%>%
  dplyr::select("effsize")
)%>%
    knitr::kable(.,caption = "Comparison of explicit & ocular confidence contrling for prev acc and p. choice",digits = 3)

```


### SM analysis is extended back to additional lags
Let's start by looking at Exp 3 and  comparing explicit and ocular 3 trials back

```{r}
# --- Data Preparation Chunk ---

conf_by_prev_trial_exp3_lag3_tbt <- mean_gz_prereg_exp3 %>%
  dplyr::group_by(sub_name) %>%
  dplyr::mutate(
    prev_gz_conf_l1 = dplyr::lag(z_gz_conf),
    prev_expl_conf_l1 = dplyr::lag(z_conf_rating),
    prev_gz_conf_l2 = dplyr::lag(z_gz_conf, 2),
    prev_expl_conf_l2 = dplyr::lag(z_conf_rating, 2),
    prev_gz_conf_l3 = dplyr::lag(z_gz_conf, 3),
    prev_expl_conf_l3 = dplyr::lag(z_conf_rating, 3),
    lag_trial_consec = dplyr::lag(is_trial_consec),
    lag2_trial_consec = dplyr::lag(is_trial_consec, 2)
  ) %>%
  dplyr::relocate(prev_gz_conf_l1, .after = z_gz_conf) %>%
  dplyr::relocate(prev_expl_conf_l1, .after = z_conf_rating) %>%
  dplyr::filter(is_trial_consec == 1) %>%
  dplyr::filter(lag_trial_consec == 1) %>%
  dplyr::filter(lag2_trial_consec == 1) %>%
  tidyr::drop_na(prev_gz_conf_l1, prev_gz_conf_l2, prev_gz_conf_l3, 
                 prev_expl_conf_l1, prev_expl_conf_l2, prev_expl_conf_l3)

# Function to run the model and tidy results safely
run_autocorr <- function(df, outcome_var, predictor_prefix) {
  df %>%
    dplyr::group_by(sub_name) %>%
    tidyr::nest() %>%
    dplyr::mutate(
      model = purrr::map(data, ~ lm(as.formula(paste(outcome_var, "~", 
                                                    paste0(predictor_prefix, 1:3, collapse = "+"))), data = .x)),
      results = purrr::map(model, broom::tidy)
    ) %>%
    tidyr::unnest(results) %>%
    dplyr::filter(term != "(Intercept)") %>%
    dplyr::mutate(
      lag = as.numeric(stringr::str_remove(term, predictor_prefix)),
      autocorr_val = as.numeric(estimate) # Force numeric type here
    ) %>%
    dplyr::select(sub_name, lag, autocorr_val) %>%
    tidyr::drop_na(autocorr_val) # Remove any failed model estimates
}

expl_conf_autocorrelation_l3 <- run_autocorr(conf_by_prev_trial_exp3_lag3_tbt, "z_conf_rating", "prev_expl_conf_l") %>%
  dplyr::mutate(source = "expl", exp_name = "Exp. 3")

gz_conf_autocorrelation_l3 <- run_autocorr(conf_by_prev_trial_exp3_lag3_tbt, "z_gz_conf", "prev_gz_conf_l") %>%
  dplyr::mutate(source = "gaze", exp_name = "Exp. 3")

all_conf_autocorrelation_l3 <- dplyr::bind_rows(expl_conf_autocorrelation_l3, gz_conf_autocorrelation_l3)


# --- Stats Chunk ---

# 1. Perform T-tests
t_results <- all_conf_autocorrelation_l3 %>%
  dplyr::group_by(source, lag) %>%
  rstatix::t_test(autocorr_val ~ 1, mu = 0) %>%
  dplyr::select(source, lag, statistic, df, p)

# 2. Perform Cohen's d
d_results <- all_conf_autocorrelation_l3 %>%
  dplyr::group_by(source, lag) %>%
  rstatix::cohens_d(autocorr_val ~ 1, mu = 0) %>%
  dplyr::select(source, lag, effsize)

# 3. Get Summary Stats (Mean and CI)
summary_stats <- all_conf_autocorrelation_l3 %>%
  dplyr::group_by(source, lag) %>%
  rstatix::get_summary_stats(autocorr_val, type = "mean_ci")

# 4. Join all and display
t_results %>%
  dplyr::left_join(d_results, by = c("source", "lag")) %>%
  dplyr::left_join(summary_stats, by = c("source", "lag")) %>%
  dplyr::mutate(p = dplyr::if_else(p < .001, "< .001", as.character(round(p, 3)))) %>%
  knitr::kable(digits = 3, caption = "Exp. 3 Autocorrelation by Lag & Source ")
```



So we see that expl. conf ratings are signfucantly autocorrelated for lag 2 too!


### Fig. 4D: divergence rate of eye & explicit by P.choice


```{r prep data to look at divergence rate by p choice fixed intervals with p choice by eye and resp}
# binning prediction gz streng by pecentile
##explicit
dive_by_expl_pchoice_interval_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(pchoice_interval=findInterval(expl.RWS.p_choice,seq(0,1,by=0.25),left.open=TRUE))%>%
  dplyr::relocate(pchoice_interval,.after = expl.RWS.p_choice)%>%
  dplyr::group_by(exp_name,sub_name,pchoice_interval,eye_resp_match)%>%
  dplyr::summarize(count=n())%>%
  dplyr::group_by(exp_name,sub_name,pchoice_interval)%>%
  dplyr::mutate(count_bin=sum(count))%>%
  dplyr::filter(eye_resp_match=="diff")%>%
  dplyr::mutate(porp_diff=count/count_bin)%>%
  dplyr::select(-c(eye_resp_match))%>%
  dplyr::mutate(source="explicit")


# binning prediction gz streng by pecentile
##explicit
dive_by_eye_pchoice_interval_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(pchoice_interval=findInterval(eye.RWS.p_choice,seq(0,1,by=0.25)),left.open=TRUE)%>%
  dplyr::relocate(pchoice_interval,.after = eye.RWS.p_choice)%>%
  dplyr::group_by(exp_name,sub_name,pchoice_interval,eye_resp_match)%>%
  dplyr::summarize(count=n())%>%
  dplyr::group_by(exp_name,sub_name,pchoice_interval)%>%
  dplyr::mutate(count_bin=sum(count))%>%
  dplyr::filter(eye_resp_match=="diff")%>%
  dplyr::mutate(porp_diff=count/count_bin)%>%
  dplyr::select(-c(eye_resp_match))%>%
  dplyr::mutate(source="eye")


dive_by_source_pchoice_interval_grp<-bind_rows(dive_by_expl_pchoice_interval_sbs,dive_by_eye_pchoice_interval_sbs)%>%
  drop_na(pchoice_interval)%>%
  dplyr::mutate(porp_diff=porp_diff*100)%>%
  dplyr::group_by(source,pchoice_interval)%>%
  dplyr::summarise(m_diff=CI(porp_diff)[2],lo_ci=CI(porp_diff)[1],hi_ci=CI(porp_diff)[3])


```

#### let's look at exploratory vs. exploitation

```{r prep data to look at conv_diver by explor_exploit}
#get subject by subject
dive_by_explor_exploit_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::rowwise()%>%
  dplyr::mutate(explor_exploit=if_else(expl.RWS.p_choice<.5,"explor","exploit"))%>%
  mutate(explor_exploit = factor(explor_exploit, levels = c("exploit", "explor"))) %>%
  count(sub_name,explor_exploit,eye_resp_match, .drop = FALSE) %>%
  group_by(sub_name,explor_exploit)%>%
  dplyr::mutate(porp=n/sum(n))%>%
  dplyr::filter(eye_resp_match=="diff")%>%
  drop_na(explor_exploit)


# group stats
dive_by_explor_exploit_group<-dive_by_explor_exploit_sbs%>%
  # dplyr::select(-n)%>%
  drop_na(explor_exploit)%>%
  dplyr::group_by(explor_exploit)%>%
  dplyr::mutate(porp=porp*100)%>%
  rstatix::get_summary_stats(porp,type = c("mean_ci"))%>%
  dplyr::mutate(lo_ci=mean-ci,hi_ci=mean+ci)

knitr::kable(dive_by_explor_exploit_group,caption="summary stats mean diverge by explor/exploit",digits=3)

# run paired ttest

#make sure that every subject has both exploration & exploitation
dive_by_explor_exploit_sbs<-dive_by_explor_exploit_sbs%>%
  dplyr::group_by(sub_name)%>%
  dplyr::filter(n()==2)


ttest_dive_by_explor_exploit<-t.test(data=dive_by_explor_exploit_sbs,
                                     porp~explor_exploit,paired = TRUE)%>%
  tidy()%>%
  dplyr::select(statistic,p.value,parameter)%>%
  dplyr::mutate(ES=rstatix::cohens_d(formula=porp~explor_exploit,
                                     data=dive_by_explor_exploit_sbs%>%
                                       dplyr::ungroup(), paired=TRUE)$effsize)

knitr::kable(ttest_dive_by_explor_exploit,caption="paired ttest of diverge by explor/exploit",digits=4)

```


```{r viz Fig. 4D divergence rate by p choice fixed intervals with p choice by eye and resp}

#modify data for plotting
dive_by_source_pchoice_interval_grp<-dive_by_source_pchoice_interval_grp%>%
  dplyr::mutate(pchoice_interval_graph=pchoice_interval-.5)%>%
  dplyr::filter(source=="explicit")

(plot_fig_5D<-
  ggplot(data=dive_by_source_pchoice_interval_grp,
         aes(x=pchoice_interval_graph,y=m_diff,color=source,fill=source))+
    geom_point(aes(y=m_diff,color=source),size=3)+
    geom_path(aes(y=m_diff,color=source),size=1.5,alpha=.8,linewidth=1.5)+
    geom_pointrange(aes(ymax=hi_ci,ymin=lo_ci),linewidth=2,fatten=2)+
    scale_fill_manual(values = color_vec_eye_expl_source)+
    scale_color_manual(values = color_vec_eye_expl_source)+
    # ylim(c(0,100))+
    scale_x_continuous(name="P. Choice ",breaks=c(0:4),
                       # labels=c("0 -.25",".25 -.50",".50 -.75",".75 - 1")
                       labels=c("0 ",".25",".50",".75","1"),limits=c(0,4)
    )+
    
    # scale_x_continuous(name="P. Choice [binned]",breaks=c(0:4),
    #                    labels=c("0",".25",".50",".75","1"))+
    labs(y= "% Response Divergence"
    )+
    geom_vline(xintercept = 2,linetype=2,color="darkgrey",linewidth=1.5)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none")
)



# ggsave(filename=file.path(path_export_main_pics,"plot_fig_4D_explicit_only.pdf"),plot=plot_fig_5D,width=16,height=16,dpi=600, units="cm",device = "pdf")

```



Here we look whether response accuracy tends to be higher when eye/explicit responses converge vs. diverge


```{r prep data to look at overall acc by converge_divergen}
acc_by_eye_resp_conv_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1", "Exp. 2"))%>%
  dplyr::group_by(exp_name,sub_name,eye_resp_match)%>%
  dplyr::summarise(rule_acc_resp=mean(resp_rule_acc),
                   rule_acc_eye=mean(eye_rule_acc))%>%
  pivot_longer(cols = c(rule_acc_resp,rule_acc_eye),names_to = "source",values_to = "acc",names_prefix = "rule_acc_")


#getting summary stats

acc_by_eye_resp_conv_by_exp<-acc_by_eye_resp_conv_sbs%>%
  dplyr::group_by(exp_name,eye_resp_match,source)%>%
  dplyr::summarise(mean_acc=CI(acc)[2],lo_ci=CI(acc)[3],hi_ci=CI(acc)[1])

acc_by_eye_resp_conv_acrss_exp<-acc_by_eye_resp_conv_sbs%>%
  dplyr::group_by(eye_resp_match,source)%>%
  dplyr::summarise(mean_acc=CI(acc)[2],lo_ci=CI(acc)[3],hi_ci=CI(acc)[1])%>%
  dplyr::mutate(exp_name="Exp.1&2")

acc_by_eye_resp_conv_grp<-bind_rows(acc_by_eye_resp_conv_by_exp,acc_by_eye_resp_conv_acrss_exp)

knitr::kable(acc_by_eye_resp_conv_grp,caption="summary stats of acc by conv/div & source", digits= 3)


## Run paired ttest
t_test_acc_by_eye_resp_conv<-t.test(formula=acc~eye_resp_match,
                                    data=acc_by_eye_resp_conv_sbs%>%
                                      dplyr::filter(source=="resp")%>%
                                      dplyr::ungroup(),
                                    paired=TRUE
)%>%
  tidy()%>%
  dplyr::select(statistic,p.value,parameter)%>%
  dplyr::mutate(ES=rstatix::cohens_d(formula=acc~eye_resp_match,
                                     data=acc_by_eye_resp_conv_sbs%>%
                                       dplyr::filter(source=="resp")%>%
                                       dplyr::ungroup(), paired=TRUE)$effsize)

knitr::kable(t_test_acc_by_eye_resp_conv,caption = "ttest results of resp acc by conv/diver",digits=4)
```
### SM figure S10: 
diverge % by explore/exploit trials P. Choice

```{r viz Plot SM figure S10}
#get divergence rate by explicit P choice
dive_by_explor_exploit_expl_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::rowwise()%>%
  dplyr::mutate(explor_exploit=if_else(expl.RWS.p_choice<.5,"explor","exploit"))%>%
  mutate(explor_exploit = factor(explor_exploit, levels = c("exploit", "explor"))) %>%
  count(sub_name,explor_exploit,eye_resp_match, .drop = FALSE) %>%
  group_by(sub_name,explor_exploit)%>%
  dplyr::mutate(dive_porp=n/sum(n))%>%
  dplyr::filter(eye_resp_match=="diff")%>%
  drop_na(explor_exploit)%>%
  dplyr::mutate(source="Explicit")%>%
  dplyr::select(-c(eye_resp_match,n))


#get divergence rate by Ocular P choice
dive_by_explor_exploit_gaze_sbs<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 1","Exp. 2"))%>%
  dplyr::rowwise()%>%
  dplyr::mutate(explor_exploit=if_else(eye.RWS.p_choice<.5,"explor","exploit"))%>%
  mutate(explor_exploit = factor(explor_exploit, levels = c("exploit", "explor"))) %>%
  count(sub_name,explor_exploit,eye_resp_match, .drop = FALSE) %>%
  group_by(sub_name,explor_exploit)%>%
  dplyr::mutate(dive_porp=n/sum(n))%>%
  dplyr::filter(eye_resp_match=="diff")%>%
  drop_na(explor_exploit)%>%
  dplyr::mutate(source="Gaze")%>%
  dplyr::select(-c(eye_resp_match,n))


dive_by_explor_exploit_comb_sbs<-bind_rows(dive_by_explor_exploit_expl_sbs,
                                           dive_by_explor_exploit_gaze_sbs)%>%
  dplyr::arrange(sub_name)%>%
  dplyr::mutate(dive_porp=dive_porp*100)


ttest_dive_by_expl_explor_exploit<-t.test(data=dive_by_explor_exploit_comb_sbs%>%
                                            dplyr::filter(source=="Explicit")%>%
                                            dplyr::group_by(sub_name)%>%
                                            dplyr::filter(n()==2)%>%
                                            dplyr::ungroup(),
                                     dive_porp~explor_exploit,paired = TRUE)%>%
  tidy()%>%
  dplyr::select(statistic,p.value,parameter)%>%
  dplyr::mutate(ES=rstatix::cohens_d(formula=dive_porp~explor_exploit,
                                     data=dive_by_explor_exploit_comb_sbs%>%
                                            dplyr::filter(source=="Explicit")%>%
                                            dplyr::group_by(sub_name)%>%
                                            dplyr::filter(n()==2)%>%
                                            dplyr::ungroup(),
                                     
                                     paired=TRUE)$effsize,
                'p. Choice source'="Explicit")


ttest_dive_by_gaze_explor_exploit<-t.test(data=dive_by_explor_exploit_comb_sbs%>%
                                            dplyr::filter(source=="Gaze")%>%
                                            dplyr::group_by(sub_name)%>%
                                            dplyr::filter(n()==2)%>%
                                            dplyr::ungroup(),
                                     dive_porp~explor_exploit,paired = TRUE)%>%
  tidy()%>%
  dplyr::select(statistic,p.value,parameter)%>%
  dplyr::mutate(ES=rstatix::cohens_d(formula=dive_porp~explor_exploit,
                                     data=dive_by_explor_exploit_comb_sbs%>%
                                            dplyr::filter(source=="Gaze")%>%
                                            dplyr::group_by(sub_name)%>%
                                            dplyr::filter(n()==2)%>%
                                            dplyr::ungroup(),
                                     
                                     paired=TRUE)$effsize,
                'p. Choice source'="Gaze")


knitr::kable(bind_rows(ttest_dive_by_expl_explor_exploit,ttest_dive_by_gaze_explor_exploit),
             caption="paired ttest of diverge by explor/exploit by pchoice different source",digits=3)


## Viz
(
  plot_SM_fig_S13<-
    ggpaired(data =dive_by_explor_exploit_comb_sbs,
                           x="explor_exploit", y="dive_porp", id="sub_name", fill="explor_exploit",line.color = "lightgrey",alpha=.1,line.size = .2 )+
    scale_x_discrete(name="Choice Strategy",labels=c("exploit"="Exploitatioin", "explor"="Exploration"),limits=c("explor","exploit"))+
    # ylim(c(0,100))+
    
    ylab("% Divergence Trails")+
    scale_fill_manual(values = c("darkorchid3","darkolivegreen3"))+
    
    theme_classic()+

    facet_wrap(~source)+
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          legend.position = "none",
          strip.background = element_blank(),
               strip.text = element_text(size = 16,face="bold")

          )
)

# ggsave(plot = plot_SM_fig_S13,filename = file.path(path_export_sm_pics,"SM_fig_S13.jpg"))

```


### Figue S11 Accurcy on Diverging and converging trials

```{r viz Figue S11 Accurcy on Diverging and converging trials}

acc_by_eye_resp_conv_sbs<-acc_by_eye_resp_conv_sbs%>%
  dplyr::mutate(acc=acc*100)
(
  plot_SM_fig_S12<-
    ggpaired(data =acc_by_eye_resp_conv_sbs%>%dplyr::filter(source=="resp"),
                           x="eye_resp_match", y="acc", id="sub_name", fill="eye_resp_match",line.color = "lightgrey",alpha=.1,line.size = .2 )+
    scale_x_discrete(name="Explicit - Ocular",labels=c("same"="Converge", "diff"="Diverge"),limits=c("same","diff"))+
    # ylim(c(0,100))+
    
    ylab("% Correct")+
    scale_fill_manual(values = c("#CCCCCC","#707070"))+
    
    theme_classic()+
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          legend.position = "none"
          )
)

# 
# # Panel B- lookat Gaze accuracy
# 
# (
#   plot_SM_fig_S12B<-
#     ggpaired(data =acc_by_eye_resp_conv_sbs%>%dplyr::filter(source=="eye"),
#                            x="eye_resp_match", y="acc", id="sub_name", fill="eye_resp_match",line.color = "lightgrey",alpha=.1,line.size = .2 )+
#     scale_x_discrete(name="Explicit - Ocular",labels=c("same"="Converge", "diff"="Diverge"),limits=c("same","diff"))+
#     ylab("% Correct (Gaze)")+
#         ylim(c(0,100))+
# 
#     scale_fill_manual(values = c("#CCCCCC","#707070"))+
#     
#     theme_classic()+
#     theme(axis.text.y =element_text(size=14),
#           axis.title.y=element_text(size=16,face="bold"),
#           axis.text.x =element_text(size=14), 
#           axis.title.x=element_text(size=16,face="bold"),
#           legend.position = "none"
#           )
# )


# ggsave(plot = plot_SM_fig_S12,filename = file.path(path_export_sm_pics,"SM_fig_S12.jpg"))
# ggsave(plot = plot_SM_fig_S12B,filename = file.path(path_export_sm_pics,"SM_fig_S12B.jpg"))

```




## SM Fig S12-16
These are additional analyses of Pre-Registartion of Exp. 3

### Hypothesis H3a: Confidence decreases following errors: 
From the pre-reg "we anticipate that confidence will decrease after trials in which the participant’s response was incorrect as opposed to correct. This will be tested across participants using a paired t-test to compare confidence ratings following previous trials in which the response was correct/incorrect"

```{r prep data to examine in exp 3 whether confidence is reduced following an error( H3a of pre-reg)}
conf_prev_acc_ps<-mean_gz_prereg_csv%>%
  dplyr::filter(exp_name%in%c("Exp. 3"))%>%
  dplyr::rowwise()%>%
  dplyr::filter(!is.na(prev_acc))%>%
  dplyr::group_by(sub_name,prev_acc)%>%
  dplyr::summarise(m_conf=mean(conf_rating))


#for each experiment seperately
smry_stats_conf_prev_acc<-conf_prev_acc_ps%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(diff_conf=m_conf-first(m_conf))%>%
  dplyr::filter(diff_conf!=0)%>%
  dplyr::ungroup()%>%
  dplyr::summarise(mean_diff=CI(diff_conf)[2],lo_ci=CI(diff_conf)[3],hi_ci=CI(diff_conf)[1],
                   t=t.test(diff_conf,mu=0)$statistic,df=t.test(diff_conf,mu=0)$parameter, p.val=t.test(diff_conf,mu=0)$p.value, ES=one_sample_ttest_cohen_d(diff_conf))


knitr::kable(smry_stats_conf_prev_acc,digits=2,caption = "smry stats conf by prev. trial acc")

```

#### Fig. S12A

```{r visualize group  data confidence after mistakes}
#Vizulaize

(
  plot_SM_fig_S14<-
    ggpaired(data =conf_prev_acc_ps,
             x="prev_acc", y="m_conf", id="sub_name", fill="prev_acc" )+
    scale_x_discrete(name= "previous trial accuracy",labels=c("error","correct"))+
    scale_fill_discrete(name= "previous trial accuracy",labels=c("error","correct"))+
    
    scale_y_continuous(name="Confidence")+
    # ggtitle("Explicit confidence ratings by previous trial's ACC",
    #         subtitle = sprintf("diff= %.3f, p= %.3f, Cohen's d'= %.3f",
    #                            t.test(data=conf_prev_acc_ps, m_conf~prev_acc, paired=TRUE)$estimate,
    #                            t.test(data=conf_prev_acc_ps, m_conf~prev_acc, paired=TRUE)$p.value,
    #                            cohens_d(data=conf_prev_acc_ps%>%ungroup(), m_conf~prev_acc, paired=TRUE)$effsize)+
    # scale_fill_discrete"previous trial acc"()
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          # legend.position = "none",
          strip.background = element_blank(),
          strip.text = element_text(size = 16,face="bold")
          
    )
)


# ggsave(plot = plot_SM_fig_S14,filename = file.path(path_export_sm_pics,"SM_fig_S14_exp3_conf_decrease_error.jpg"), width=15, units = "cm")
```



#### Pre reg EXP 3- H3A:  confidence learning curve
"Further supporting the idea that confidence tracks learning we expect confidence to exhibit a learning curve. Within a block (a series of trials that follow the same underlying rule), we expect normalized confidence ratings to exhibit a learning curve that is characterized by a monotonic increase during the early trials until an asymptote is reached"


``` {r prep data to examine in exp 3 whether confidence  exhibits learning curve (H3a of pre-reg) }
#subject by subject relative accuracy-binned
sbs_rel_trial_conf_bin<-mean_gz_prereg_exp3%>%
  dplyr::filter(exp_name%in%c("Exp. 3"))%>%
  dplyr::rowwise()%>%
  dplyr::mutate(bin_ind=findInterval(rel_trial_number,seq(1,36,by=4)))%>%
  dplyr::group_by(sub_name,bin_ind)%>%
  dplyr::summarize(rel_conf=mean(z_conf_rating))%>%
  dplyr::mutate(source="expl")


#group statistic-binned
sum_rel_trial_conf_bin<-sbs_rel_trial_conf_bin%>%
  dplyr::group_by(bin_ind,source)%>%
  dplyr::summarize(lo_ci=CI(rel_conf)[3],hi_ci=CI(rel_conf)[1],mean_conf=CI(rel_conf)[2])

```

#### Fig. S13B

```{r plot confidence as function of relative block number , fig.show="hold", out.width="50%"}
#plot learning within block binned by 4 trial 

( plot_SM_fig_S14B<-
  ggplot(data=sum_rel_trial_conf_bin%>%dplyr::filter(bin_ind<9),aes(x=bin_ind,y=mean_conf))+
   geom_line()+
   geom_point()+
   geom_ribbon(aes(ymin=lo_ci ,ymax=hi_ci),alpha=.3, color=NA,fill="lightgrey")+
   # geom_line(data=sbs_rel_trial_acc_bin,aes(x=bin_ind,y=rel_actual_acc,group=sub_name),alpha=.2)+
   scale_x_continuous(name=" Trial # (in block)", labels = c("1-4","5-8","9-12","13-16","17-20","21-24","25-28","29-32"),breaks = c(1:8),limit=c(1,8))+
   scale_y_continuous(name = "Confidence [z-scored]")+
   geom_hline(yintercept = 0, color="brown1",linetype="dashed")+
   
   # geom_hline(yintercept = 75, color="darkgoldenrod1",linetype="dashed")+
   # xlim(c(1,8))+
   # ggtitle("Confidence within block (binned) ")+
   theme_classic()+
   theme(axis.title.x = element_text(size = 14,face="bold"),
         axis.title.y = element_text(size = 14,face="bold"),
         axis.text.x = element_text(size = 12,angle=15),
         axis.text.y = element_text(size = 12,angle=0),
         strip.text = element_text(size = 16,face="bold"),
         plot.title=element_text(size = 16,face="bold",hjust=.5),
         legend.position = "none"
         )
 
)

# ggsave(plot = plot_SM_fig_S14B,filename = file.path(path_export_sm_pics,"SM_fig_S14B_exp3_conf_learning curve.jpg"), width=15, units = "cm")
```


### Pre-reg H3b: Confidence is increased for correct trials as opposed to incorrect trials:
In line with extensive work demonstrating human’s metacognitive abilities (Fleming & Daw, 2017; Maniscalco & Lau, 2012), we expect normalized confidence ratings to be increased for trials in which the prediction is in line with the underlying rule (i.e. rule accuracy). This will be tested across participants using a paired t-test to compare confidence on trials with correct/incorrect rule accuracy (see figure “Confidence by Rule Accuracy”). 

Figure “Confidence by Rule Accuracy”. Comparing trials by their rule accuracy, we expect that across participants the mean confidence rating will be significantly higher for correct as opposed to incorrect trials. 

```{r prep data for confidence ratings by acc}
m_conf_by_act_acc<-mean_gz_prereg_exp3%>%
  dplyr::filter(exp_name%in%c("Exp. 3"))%>%
  dplyr::group_by(sub_name,is_acc)%>%
  dplyr::summarise(m_conf=mean(conf_rating),accuracy_type="Actual")

m_conf_by_rule_acc<-mean_gz_prereg_exp3%>%
  dplyr::filter(exp_name%in%c("Exp. 3"))%>%
  dplyr::group_by(sub_name,resp_rule_acc)%>%
  
  dplyr::summarise(m_conf=mean(conf_rating),accuracy_type="Rule")%>%
    dplyr::rename(is_acc=resp_rule_acc)

m_conf_by_acc_join<-bind_rows(m_conf_by_act_acc,m_conf_by_rule_acc)


```


```{r viz confidence ratings by acc, fig.show="hold", out.width="50%"}


(plot_SM_fig_confidence_afer_error<-
  ggpaired(data=m_conf_by_acc_join,
           x="is_acc",y="m_conf",id="sub_name",fill="is_acc",line.color = "lightgrey",alpha=.1,line.size = .2)+
    scale_y_continuous(name="Confidence Rating")+
    scale_x_discrete(name="Current Trial's Accuracy",labels=c("error","correct"))+
    scale_fill_discrete(name= "Current Trial's Accuracy",labels=c("error","correct"))+
    theme_classic()+
    
    facet_wrap(~accuracy_type)+
    theme(axis.text.y =element_text(size=14),
          axis.title.y=element_text(size=16,face="bold"),
          axis.text.x =element_text(size=14), 
          axis.title.x=element_text(size=16,face="bold"),
          # legend.position = "none",
          strip.background = element_blank(),
          strip.text = element_text(size = 16,face="bold")
          
    )
)




# summary stats
m_conf_by_acc_smry_stats<-m_conf_by_acc_join%>%
  dplyr::group_by(accuracy_type,is_acc)%>%
  rstatix::get_summary_stats(m_conf,type="mean_ci")%>%
  dplyr::mutate(lo_ci=mean-ci,hi_ci=mean+ci)

#statistiacl test

m_conf_by_acc_smry_cmpr_stats<-dplyr::full_join(
  m_conf_by_acc_join%>%
  dplyr::arrange(accuracy_type,sub_name,is_acc)%>%
  dplyr::group_by(accuracy_type)%>%
  rstatix::t_test(m_conf~is_acc,paired = TRUE)%>%
  dplyr::select(accuracy_type,statistic,df,p),
  m_conf_by_acc_join%>%
  dplyr::arrange(accuracy_type,sub_name,is_acc)%>%
  dplyr::group_by(accuracy_type)%>%
  rstatix::cohens_d(m_conf~is_acc,paired = TRUE)%>%
    dplyr::select(accuracy_type,effsize),
  by="accuracy_type")
    

knitr::kable(m_conf_by_acc_smry_stats,digits=2,caption = "smry stats  conf by trial acc")

knitr::kable(m_conf_by_acc_smry_cmpr_stats,digits=3,caption = "stats tests conf by trial acc")
  

```


### Pre reg EXP 3: H3c: Explicit confidence & RW trajectory

"H3C: Confidence tracks the latent variable of previous trial’s Prediction Error (derived from R-W Model): In accordance with Hypothesis 3a, which states that confidence ratings will be updated by the previous trial's accuracy, and in line with previous research that has found that confidence ratings track internal learning processes (Meyniel et al., 2015), we expect confidence ratings to be significantly correlated with the previous trial's absolute prediction error.
To test this for each participant we will correlate the trial’s Confidence Rating and the previous trial’s Prediction Error. We will then run a one-sample t-test on the participants' Pearson correlations’ distribution. We hypothesize that the distribution will be significantly greater than zero and moderate . 
In addition to the previous trial’s prediction error as an exploratory analysis we will examine confidence rating’s correlation to the probability associated with the choice made (P. Choice) and the strength of the value associated with the choice (v; this is quantified as the distance of v from 0.5), that are also derived from the R-W model. "



```{r prep data for H3c: correltaion between RW traj & confidence ratings}

corr_PC_conf_ps<-mean_gz_prereg_exp3%>%
  dplyr::group_by(sub_name)%>%
  # drop_na(expl.RWS.p_choice,expl.RWS.prev_delta,conf_rating,expl.RWS.dist_v_5)%>%
  dplyr::summarize(r.conf_PC=rcorr(conf_rating,expl.RWS.p_choice)$r[2],pval.conf_PC=rcorr(conf_rating,expl.RWS.p_choice)$P[2],
                   r.conf_prev_delta=rcorr(conf_rating,expl.RWS.prev_delta)$r[2],pval.conf_prev_delta=rcorr(conf_rating,expl.RWS.prev_delta)$P[2],
                    r.conf_dist_v=rcorr(conf_rating,expl.RWS.dist_v_5)$r[2],pval.conf_dist_v=rcorr(conf_rating,expl.RWS.dist_v_5)$P[2]
  )



#doing for pval
p_val_corr_PC_conf_long<-corr_PC_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("pval")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


# doing for corr
corr_val_PC_conf_long<-corr_PC_conf_ps%>%
  dplyr::select(c(sub_name,starts_with("r")))%>%
  pivot_longer(!sub_name,names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")


##all subjects
sum_p_val_PC_conf=p_val_corr_PC_conf_long%>%
    drop_na(val)%>%
  group_by(vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig),total_sub=n())


sum_corr_conf_rating_rw_traj<-corr_val_PC_conf_long%>%
  group_by(vars_compared)%>%
  drop_na(val)%>%
  dplyr::summarise(mean_corr=CI(val)[2],hi_CI=CI(val)[1],lo_CI=CI(val)[3],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                    ES=one_sample_ttest_cohen_d(val)
                   )%>%
  full_join(.,sum_p_val_PC_conf,by="vars_compared")

knitr::kable(sum_corr_conf_rating_rw_traj,digits = 3, caption = "correlation Confidence Ratings  and RWS learning metrics")

```

#### Fig. S13

```{r viz correlation of H3c: correltaion between RW traj & confidence ratings}
#all subjects
corr_conf_RWS<-corr_val_PC_conf_long%>%
  dplyr::filter(vars_compared%in%c("conf_PC","conf_prev_delta"))%>%
  dplyr::filter(value_type=="corr")

grp_corr_conf_RWS<-corr_conf_RWS%>%
  dplyr::group_by(vars_compared)%>%
  dplyr::summarize(grp_mean=CI(val)[2],lo_ci=CI(val)[1],hi_ci=CI(val)[3])



(
  plot_SM_fig_S15<-
    ggplot(data=corr_conf_RWS,aes(y=val,x=1))+
    #         xlim(c(.5,1.5))+
    # ylim(c(-.1,.3))+
       geom_boxplot(outlier.shape = NA,linewidth=1,color="black",size=.5,width=.4)+ #,width=.02
 
    geom_point(color="#707070",position = position_jitter(width=.1),size=3, alpha = .8)+
    
    # geom_hline(yintercept = 0, color="red",linetype="solid",size=1.5)+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
ylab(expression(atop(rho, "value")))+

    theme_classic()+
    # coord_fixed(ratio = 4,xlim = c(0.8, 1.2))+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          strip.background = element_blank(),
          legend.position = "none"
    )+
    facet_wrap(~vars_compared)
  
)

# ggsave(plot = plot_SM_fig_S15,filename = file.path(path_export_sm_pics,"SM_fig_S15_exp3_corr_conf_RWS_traj.jpg"), width=15, units = "cm")
```


### Exp 3: Pre_reg Hypothesis 4
####4A Gaze is associated with explicot prediction
Hypothesis 4a: Gaze direction is strongly associated with the direction of the explicit prediction: To examine how explicit responses and implicit ocular expectations are related, we will take the normalized gaze direction of the first 300 msec in the environment (see Figure “Association Between Explicit Predictions and Gaze” left panel) and average it per trial and per Prediction (right/ left). We then compare the effect of explicit Prediction on Normalized Gaze across participants using a paired t-test (see Figure “Association Between Explicit Predictions and Gaze”   right panel).  We expect a significant effect of Prediction on Normalized Gaze.

``` {r prep data for H4A experiment 3}
#summarizing per trial (pt) and then summing across trials (may be more robust to outliers)


exp3_mean_gz_by_pred<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name,QuestionResult)%>%
  dplyr::summarize(lo_ci=CI(m_gz)[3],hi_ci=CI(m_gz)[1],mean_gz=CI(m_gz)[2])

```

#### Fig. S14A
```{r viz gaze follows prediction  ggpaired experiment 3}
## plotting ggpaired

(
  plot_SM_fig_S16A_ggpaired_gz_by_pred<-
    ggpaired(data =exp3_mean_gz_by_pred,
             x="QuestionResult", y="mean_gz", id="sub_name", fill="QuestionResult" , line.color = "lightgrey",line.size = .2)+
    scale_x_discrete(name= "Prediction",labels=c("L","R"))+
    # scale_x_discrete(name= "",labels=c("L","R"))+

    ylab("Gaze Direction")+
    scale_fill_manual(values=c("plum4","seagreen4"),labels=c("left","right"),name= "Prediction")+
    # ggtitle("Gaze by Prediction (per trial)",
    #         subtitle=sprintf("p: %.3f Cohen's d: %.3f", t.test(data=mean_gz_by_pred, mean_gz~QuestionResult, paired=TRUE)$p.val, 
    #                          cohens_d(data=mean_gz_by_pred%>%ungroup(), mean_gz~QuestionResult, paired=TRUE)$effsize))+
    # ylim(c(-.95,.9))+
    theme_classic()+
    theme(axis.title.y = element_text(size = 16,face="bold"),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
            # legend.position = "right",
          legend.position = "none",
          )
)

#Summary stats seperately
exp3_smry_stats_mean_gz_by_pred<-exp3_mean_gz_by_pred%>%
  dplyr::group_by(sub_name)%>%
  dplyr::mutate(diff_gz=mean_gz-first(mean_gz))%>%
  dplyr::filter(diff_gz!=0)%>%
  dplyr::ungroup()%>%
  dplyr::summarise(mean_diff=CI(diff_gz)[2],lo_ci=CI(diff_gz)[3],hi_ci=CI(diff_gz)[1],
                   t=t.test(diff_gz)$statistic,df=t.test(diff_gz)$parameter, p.val=t.test(diff_gz)$p.value
                   , ES=one_sample_ttest_cohen_d(diff_gz))





knitr::kable(exp3_smry_stats_mean_gz_by_pred,
             digits=2,caption = "Diff gaze direction by prediction Exp 3 (pre-reg)")




# ggsave(plot = plot_SM_fig_S16A_ggpaired_gz_by_pred,filename = file.path(path_export_sm_pics,"SM_fig_S16A_exp3_ggpaired_gz_by_pred.jpg"), width=15, units = "cm")



```

#### Fig. S14B
```{r Exp 3 gaze by prediction indov subjects}


#fix up subjects name
exp3_mean_gz_by_pred<-exp3_mean_gz_by_pred%>%
  dplyr::mutate(new_sub_name=sprintf("Sub %.2d",parse_number(sub_name)))

( plot_SM_fig_S16B_gz_diff_indiv<-
    ggplot(data=exp3_mean_gz_by_pred,aes(x=mean_gz,y=new_sub_name,color=as.factor(QuestionResult)))+ #y=fct_reorder(sub_name, desc(sub_num)
    geom_pointrange(aes(xmin=lo_ci,xmax=hi_ci),position=position_dodge(width = .3))+
    geom_vline(xintercept = 0,color="brown1",linetype="dashed")+
    scale_color_manual(name="Prediction",values=c("plum4","seagreen4"),labels=c("left","right"))+
    # facet_col(~exp_name,scales = "free_y")+
    ylab("Subject")+
    xlab("Gaze Direction")+
    theme_classic()+
    theme(axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 8,angle=0),
          )
  # ggtitle("Gaze by Prediction ")
  
  
)

exp3_gz_by_pred_stats<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarise(p=t.test(m_gz~QuestionResult)$p.value,
                   is_sig=if_else(p<.05,1,0))

gz_by_pred_stats_per_exp<-exp3_gz_by_pred_stats%>%
  dplyr::summarise(n_sig=sum(is_sig), total_n=n())

kable(gz_by_pred_stats_per_exp,caption = "Gaze by Prediction, single ss signfiacne")
# ggsave(plot = plot_SM_fig_S16B_gz_diff_indiv,filename = file.path(path_export_sm_pics,"SM_fig_S16B_exp3_gz_by_pred_indiv_ss.jpg"), width=15, units = "cm")
```

### H4: A gaze Prediction is correlated to P. Choice
```{r exp 3 prep data for correlation of gaze prediction and sRW traj}

# getting correlation of gaze & RW trajectory (this is done on trial by-trial basis ) per subject
exp3_corr_gz_rws_traj_ps<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(
    # corr pred_gz& previous trial's PE
    r.da_pred_gz=rcorr(expl.RWS.prev_delta,m_pred_gz)$r[2],pval.da_pred_gz=rcorr(expl.RWS.prev_delta,m_pred_gz)$P[2], 
    
    #  gaze2prediction & dist of v from 0.5
    r.distv5_pred_gz=rcorr(expl.RWS.dist_v_5,m_pred_gz)$r[2],pval.distv5_pred_gz=rcorr(expl.RWS.dist_v_5,m_pred_gz)$P[2], # corr pred_gz 
    
    #  gaze2prediction & P Choice
    r.PC_pred_gz=rcorr(expl.RWS.p_choice,m_pred_gz)$r[2],pval.PC_pred_gz=rcorr(expl.RWS.p_choice,m_pred_gz)$P[2] 
  )

#pivoting to long (this is done very rudimentary)

#doing for pval
exp3_p_val_long_rws<-exp3_corr_gz_rws_traj_ps%>%
  dplyr::select(c(exp_name,sub_name,starts_with("pval")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "pval.",values_to="val")%>%
  dplyr::mutate(value_type="p.val")%>%
  dplyr::mutate(is_sig=if_else(val<.05,1,0))


# doing for corr
exp3_corr_val_long_rws<-exp3_corr_gz_rws_traj_ps%>%
  dplyr::select(c(exp_name,sub_name,starts_with("r")))%>%
  pivot_longer(!c(exp_name,sub_name),names_to = "vars_compared",names_prefix = "r.",values_to="val")%>%
  dplyr::mutate(value_type="corr")

# getting numbeer of sig subjects
exp3_sum_p_val_rws=exp3_p_val_long_rws%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(n_sig=sum(is_sig,na.rm = TRUE),total_sub=n())

#joining
exp3_sum_corr_gz_rws_traj<-exp3_corr_val_long_rws%>%
  group_by(exp_name,vars_compared)%>%
  dplyr::summarise(mean_corr=CI(val)[2],lo_corr=CI(val)[1],hi_corr=CI(val)[3],
                   group_t_statistic=t.test(val)$statistic, group_pval=t.test(val)$p.value,
                   ES=one_sample_ttest_cohen_d(val))%>%
  full_join(.,sum_p_val_rws,by=c("exp_name","vars_compared"))

knitr::kable(exp3_sum_corr_gz_rws_traj%>%dplyr::filter(exp_name=="Exp. 3"),digits = 3, caption = "EXP 3correlation EM and learning metric RW (PreReg sub)")
```
#### Fig. S15

```{r EXP3 visualize distribution of correlation value, fig.show="hold", out.width="50%"}
#all subjects
exp3_corr_pc_gz2pred_rws<-exp3_corr_val_long_rws%>%
  dplyr::filter(vars_compared=="PC_pred_gz")%>%
  dplyr::filter(value_type=="corr")

exp3_grp_corr_pc_gz2pred_rws<-exp3_corr_pc_gz2pred_rws%>%
  dplyr::group_by(exp_name)%>%
  dplyr::summarize(grp_mean=CI(val)[2],lo_ci=CI(val)[1],hi_ci=CI(val)[3])

(
  SM_plot_corr_gz_pred_pchoice<-
    ggplot(data=exp3_corr_pc_gz2pred_rws,aes(y=val,x=1))+
    # geom_violin(alpha=.4,scale="width")+
        xlim(c(.5,1.5))+

    geom_boxplot(outlier.shape = NA,linewidth=1,color="black",size=.5,width=.4)+ #,width=.02
    # geom_pointrange (data=grp_corr_pc_gz2pred_rws%>%dplyr::filter(exp_name!="Exp. 3"), aes(y=grp_mean,ymin=lo_ci, ymax=hi_ci),size=3,fatten=1.5,width=.1, color="black")+
    

    geom_point(color="#707070",position = position_jitter(width=.1),size=3, alpha = .8)+
    
    # geom_hline(yintercept = 0, color="red",linetype="solid",size=1.5)+
    geom_hline(yintercept = 0, color="brown1",linetype="dashed",linewidth=1.5)+
ylab(expression(atop(rho, "\n Gaze & P. Choice")))+
    # ylab(paste(" \u03C1","Gaze & P. Choice"))+
    # ylim(c(-.3,.5))+
    
    theme_classic()+
    # coord_fixed(ratio = 4,xlim = c(0.8, 1.2))+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.y = element_text(size = 14,angle=0),
          strip.text = element_text(size = 16,face="bold"),
          strip.background = element_blank(),
          legend.position = "none"
    )+
    facet_wrap(~exp_name)
)

# ggsave(plot = SM_plot_corr_gz_pred_pchoice,filename = file.path(path_export_sm_pics,"SM_fig_S17_exp3_corr_gz_pred_pchoice.jpg"), width=15, units = "cm")
```

### H4:B Gaze fulfills benchmarks of confidence
"Hypothesis 4b: ”Gaze exhibits the three statistical hallmarks of confidence”: In brief (see https://osf.io/t49pj for full explanation), we will examine whether gaze reflects confidence and fulfills the three statistical hallmarks of confidence (Sanders et al., 2016)"

```{r Exp 3. prep data for benchmark 1 check if accuarcy increases with gaze2prediction}

#add percentile 
mean_gz_prereg_exp3<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(tile_gz2pred=ntile(m_pred_gz,n_ptiles_gz2pred))%>%
  dplyr::relocate(tile_gz2pred,.after = m_pred_gz)

#get subject by subject
exp3_sbs_acc_per_tile_gz2pred<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name,tile_gz2pred)%>%
  dplyr::summarize(m_actual_acc=mean(is_acc)*100,m_rule_acc=mean(resp_rule_acc)*100,m_gz2pred=mean(m_pred_gz),count=n())


#group- all subjects
exp3_grp_acc_per_tile_gz2pred<-exp3_sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,tile_gz2pred)%>%
  dplyr::summarize(lo_ci_act_acc=CI(m_actual_acc)[1],hi_ci_act_acc=CI(m_actual_acc)[3],m_actual_acc=CI(m_actual_acc)[2],
                   lo_ci_rule_acc=CI(m_rule_acc)[1],hi_ci_rule_acc=CI(m_rule_acc)[3],m_rule_acc=CI(m_rule_acc)[2])


```

```{r Exp. 3run prereg stats for benchmark 1}

# getting correlation of gaze & RW trajectory (this is done on trial by-trial basis ) per subject
exp3_sbs_corr_bench1_acc_gz_pred<-exp3_sbs_acc_per_tile_gz2pred%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::summarize(
    # corr rule acc & gz prediction
    r.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$r[2],pval.acc_gz_pred=rcorr(m_rule_acc,m_gz2pred,type = "spearman")$P[2]
  )%>%
  dplyr::mutate(is_sig=if_else(pval.acc_gz_pred<.05,1,0))



#joining
exp3_sum_stats_corr_bench1_acc_gz_pred <-exp3_sbs_corr_bench1_acc_gz_pred%>%
  group_by(exp_name)%>%
  dplyr::summarise(mean_corr=CI(r.acc_gz_pred)[2],lo_corr=CI(r.acc_gz_pred)[1],hi_corr=CI(r.acc_gz_pred)[3],
                   group_t_statistic=t.test(r.acc_gz_pred)$statistic, group_pval=t.test(r.acc_gz_pred)$p.value,
                   ES=one_sample_ttest_cohen_d(r.acc_gz_pred))

knitr::kable(exp3_sum_stats_corr_bench1_acc_gz_pred,digits=4, caption = "Exp 3 Conf benchmark 1 distribution of spearman correlation")
```

So this is almost sig. but not a very good way to test it...
```{r Exp3 test confidence benchmark 1 with glmer}
## RE: geberal intercept
rule_acc_by_gz_pred_frmla<-resp_rule_acc~m_pred_gz+(1|sub_name)

rule_acc_by_gz_pred.res_exp3=glmer(rule_acc_by_gz_pred_frmla,data=mean_gz_prereg_exp3,
                                   family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 3")


knitr::kable(rule_acc_by_gz_pred.res_exp1, digits = 5, caption="Conf benchmark 1 with glmer")
```

#### Fig S16A
Vizulaize benchmark 1
```{r Exp 3 visualize benchmark 1 check if accuarcy increases with gaze2prediction}
# plot rule acc  
##Exp. 3
(plot_SM_fig_S18A<-
   ggplot(data=exp3_grp_acc_per_tile_gz2pred,aes(x=tile_gz2pred, y= m_rule_acc))+
   geom_pointrange(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),color="black",linewidth=1.5)+
    geom_line(alpha=.8,linewidth=2,color="black")+
   geom_point(size=3)+
   # geom_ribbon(aes(ymin=lo_ci_rule_acc,ymax=hi_ci_rule_acc),fill="sandybrown", alpha=.2,  color=NA)+
   
   scale_x_continuous(name= ("Gaze Prediction"))+
   scale_y_continuous(name=("% Correct"),limits = c(62,86))+
   
   theme_classic()+
   theme(axis.title.x = element_text(size = 16,face="bold"),
         axis.title.y = element_text(size = 16,face="bold"),
         axis.text.x = element_text(size = 14,angle=0),
         axis.text.y = element_text(size = 14,angle=0),
         legend.position = "none"
   )
)


# ggsave(plot = plot_SM_fig_S18A,filename = file.path(path_export_sm_pics,"SM_fig_S18A_exp3_Benchmark1.jpg"), width=12, units = "cm")


```

### Fig S16B
Benchmark 2: folded X

#### Running with RWS

```{r EXP3 prep data to look at benchmark 2 of confidence using distV as proxy of evidence RWS}
n_ptiles_dist_v<-6

exp3_gz_by_distV_RWS_acc_df<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name,resp_rule_acc)%>%
  dplyr::mutate(dist_v_rule_acc_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning according to RULE ACC
  dplyr::relocate(dist_v_rule_acc_bin,.after="expl.RW.dist_v_5") %>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,n_ptiles_dist_v))%>% #binning only according to V
  dplyr::relocate(dist_v_bin,.after="dist_v_rule_acc_bin") 


```


```{r EXP3run prereg stats for Benchmark 2 using lme4 RWS }
#Exp 3
bench2_full_frmla<-m_pred_gz~resp_rule_acc+dist_v_bin+resp_rule_acc:dist_v_bin+(1|sub_name)

bench2_full_exp3.res_rws=lmer(bench2_full_frmla,data=exp3_gz_by_distV_RWS_acc_df,REML = FALSE)

# remove interaction term
bench2_null_frmla<-m_pred_gz~resp_rule_acc+dist_v_rule_acc_bin+(1|sub_name)
# bench2_null_frmla<-m_pred_gz~resp_rule_acc+dist_v_bin+(1|sub_name)

# bench2_null_frmla<-m_pred_gz~resp_rule_acc+expl.dist_v_5+(1|sub_name)

bench2_null_exp3.res_rws=lmer(bench2_null_frmla,data=exp3_gz_by_distV_RWS_acc_df,REML = FALSE)


#test with anova
bench2_aov_exp3_res_rws<-anova(bench2_full_exp3.res_rws,bench2_null_exp3.res_rws)%>%tidy()%>%mutate(exp = "Exp. 3")%>%dplyr::filter(!is.na(df))

knitr::kable(bench2_aov_exp3_res_rws, digits= 4, caption= "EXP 3. RWS lme results Benchmark 2")
```

```{r Exp 3 getting summary stats for visualization bin by v  and acc RWS}
min_trials_per_bin<-5

# summarizing across subjects
exp3_gz_by_distV_acc_grp_rws<-exp3_gz_by_distV_RWS_acc_df%>%
  dplyr::group_by(exp_name,sub_name,dist_v_rule_acc_bin,resp_rule_acc)%>%
  dplyr::summarise(m_gz2pred=mean(m_pred_gz),count=n())%>%
  dplyr::mutate(acc_type="rule")%>%
  dplyr::rename(acc=resp_rule_acc)%>%
  dplyr::filter(count>=min_trials_per_bin)%>%
  dplyr::group_by(exp_name,dist_v_rule_acc_bin,acc)%>%
  dplyr::summarise(lo_ci=CI(m_gz2pred)[1],hi_ci=CI(m_gz2pred)[3],m_gz2pred=CI(m_gz2pred)[2],n_sub=n())

```


```{r EXP3 visualize benchmark 2 for Acc as functioon of gaze confidence & v binn using v and acc RWS, fig.show="hold", out.width="50%" }
#visualize dist_v_rule acc
(
  plot_SM_fig_gz_pred_bench2<-
    ggplot(data=exp3_gz_by_distV_acc_grp_rws,
           aes(x=(dist_v_rule_acc_bin),y=m_gz2pred,color=as.factor(acc),fill=as.factor(acc), group=as.factor(acc)))+
    geom_line(aes(color=as.factor(acc)),alpha=.4,linewidth=2)+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_rule_acc_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    scale_x_continuous(name=" Expectation Strength")+
    scale_y_continuous(name = "Gaze Prediction")+
    scale_color_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    scale_fill_manual(name="ACC",values=color_vec_benchmark2_acc,labels=c("error","correct"))+
    theme_classic()+
    theme(plot.title = element_text(size = 20,face="bold",hjust = 0.5),
          axis.title.x = element_text(size = 16,face="bold"),
          axis.title.y = element_text(size = 16,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 14,angle=0),
          # legend.position = "none"
    )
)


# ggsave(plot = plot_SM_fig_gz_pred_bench2,filename = file.path(path_export_sm_pics,"SM_fig_S19_exp3_Benchmark2.jpg"), width=12, units = "cm")

```

#### Fig S16C
Confidence Benchmark 3: EXP3
```{r benchmark 3: prep data to look at  of confidence using distV RWS as proxy of evidence EXP3}
# binning prediction gz streng
exp3_acc_by_gz_distV_RWS_sbs<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  drop_na(dist_v_bin)%>%
  dplyr::group_by(exp_name,sub_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarize(acc=mean(resp_rule_acc),count=n()) 

# summarizing across subject
exp3_acc_by_gz_distV_RWS_grp<-exp3_acc_by_gz_distV_RWS_sbs%>%
  dplyr::group_by(exp_name,dist_v_bin,pred_gz_bin)%>%
  dplyr::summarise(lo_ci=CI(acc)[1]*100,hi_ci=CI(acc)[3]*100,m_acc=CI(acc)[2]*100)



```


```{r EXP 3 visualize benchmark 3 for gaze as confidence using V RWS as proxy of evidence, fig.show="hold", out.width="50%" }

#define colors for high/low gaze prediction
cvec_pred_strength<-c("black","azure3")


#Experiment 3
( plot_SM_fig_gz_pred_bench3<-
    ggplot(exp3_acc_by_gz_distV_RWS_grp,
           aes(x=(dist_v_bin),y=m_acc,color=as.factor(pred_gz_bin),fill=as.factor(pred_gz_bin), group=(dist_v_bin)))+
    geom_pointrange(aes(ymin=lo_ci,ymax=hi_ci,group=as.factor(dist_v_bin)),position = position_dodge2(width=.1),linewidth=1.5)+
    geom_line(aes(color=as.factor(pred_gz_bin),group=as.factor(pred_gz_bin)),alpha=.8,linewidth=2)+
    
    scale_x_continuous(name="Expectation Strength")+
    scale_y_continuous(name = "% Correct")+
    scale_color_manual(name="Gaze Prediction", labels=c("low","high"), values=cvec_pred_strength)+
    scale_fill_manual(name="Gaze Prediction", labels=c("low","high"), values=c("black","azure2"))+
    theme_classic()+
    theme(axis.title.x = element_text(size = 12,face="bold"),
          axis.title.y = element_text(size = 12,face="bold"),
          axis.text.x = element_text(size = 10,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          legend.position = "none"
         )
    )




# ggsave(plot = plot_SM_fig_gz_pred_bench3,filename = file.path(path_export_sm_pics,"SM_fig_S19_exp3_Benchmark3.jpg"), width=12, units = "cm")
```

```{r EXP3 prep data to run prereg stats for Benchmark 3 using lme4  bin only by v5 RWS}
exp3_acc_w_gz_distV_RWS_sbs_4stats<-mean_gz_prereg_exp3%>%
  dplyr::group_by(exp_name,sub_name)%>%
  dplyr::mutate(dist_v_bin=ntile(expl.RWS.dist_v_5,6))%>% #binning  distance of V
  dplyr::mutate(pred_gz_bin=ntile(m_pred_gz,2))%>% #binning high & low gaze2pred
  dplyr::relocate(dist_v_bin,.after="expl.RWS.dist_v_5")%>%
  dplyr::relocate(pred_gz_bin,.after="m_pred_gz")%>%
  dplyr::select("exp_name","sub_name","TrialNumber","resp_rule_acc", "pred_gz_bin","dist_v_bin")


```

```{r EXP 3 run prereg stats for Benchmark 3 using lme4  bin only by v5 RW glmer}
bench3_full_frmla<-resp_rule_acc~pred_gz_bin+dist_v_bin+pred_gz_bin:dist_v_bin+(1|sub_name)

#Exp 1
bench3_full_exp1.res_rws=glmer(bench3_full_frmla,                        
                               data=exp3_acc_w_gz_distV_RWS_sbs_4stats%>%ungroup(),
                               family = binomial)%>%
  broom.mixed::tidy()%>%
  mutate(exp_name="Exp. 1")




knitr::kable(bench3_full_exp1.res_rws%>%dplyr::filter(effect=="fixed"),caption = "Exp 3Benchmark 3 RWS (glmer)")
```



## Fig. S17 
Parameter  recovery

```{r prep_data for parameter recovery}
# pivoting to long
param_recov_long<-pivot_longer(param_recov_csv%>%dplyr::mutate(iter=row_number()),cols=!iter,names_to = c("param_status","model","param_name"),names_sep = "_",values_to = "val")

```

```{r viz param recovery}

#Visuzlaining
(plot_SM_parm_recovery_rw<-
  ggplot(data=param_recov_long%>%dplyr::filter(model=="RW")%>%
           
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val),
         aes(x=sim,y=rec))+
    xlab("Simulated Value")+
    ylab("Recovered Value")+
    geom_point(alpha=.7)+
    geom_smooth(method = "lm", se = TRUE, color = "lightblue")+
    facet_wrap(~param_name,scales = "free",labeller =  label_parsed)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          strip.text = element_text(size = 14,face="bold"),
          strip.background = element_blank()

    )
  
)


(plot_SM_parm_recovery_rws<-
  ggplot(data=param_recov_long%>%dplyr::filter(model=="RWS")%>%
           
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val),
         aes(x=sim,y=rec))+
    xlab("Simulated Value")+
    ylab("Recovered Value")+
    geom_point(alpha=.7)+
    geom_smooth(method = "lm", se = TRUE, color = "lightblue")+
    facet_wrap(~param_name,scales = "free",labeller =  label_parsed)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          strip.text = element_text(size = 14,face="bold"),
          strip.background = element_blank()

    )
  
)


(plot_SM_parm_recovery_wsls<-
  ggplot(data=param_recov_long%>%dplyr::filter(model=="WSLS")%>%
           
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val),
         aes(x=sim,y=rec))+
    xlab("Simulated Value")+
    ylab("Recovered Value")+
    geom_point(alpha=.7)+
    geom_smooth(method = "lm", se = TRUE, color = "lightblue")+
    facet_wrap(~param_name,scales = "free",labeller =  label_parsed)+
    theme_classic()+
    theme(axis.title.x = element_text(size = 14,face="bold"),
          axis.title.y = element_text(size = 14,face="bold"),
          axis.text.x = element_text(size = 14,angle=0),
          axis.text.y = element_text(size = 10,angle=0),
          strip.text = element_text(size = 14,face="bold"),
          strip.background = element_blank()

    )
  
)

# ggsave(plot = plot_SM_parm_recovery_rw,filename = file.path(path_export_sm_pics,"SM_fig_S20_plot_SM_parm_recovery_rw.jpg"), height=10, units = "cm")
# 
# ggsave(plot = plot_SM_parm_recovery_rws,filename = file.path(path_export_sm_pics,"SM_fig_S20_plot_SM_parm_recovery_rws.jpg"), height=10, units = "cm")
# 
# ggsave(plot = plot_SM_parm_recovery_wsls,filename = file.path(path_export_sm_pics,"SM_fig_S20_plot_SM_parm_recovery_wsls.jpg"), height=10, units = "cm")


```

```{r print out correlation values of parameter recovery}
param_corr_val_rw<-param_recov_long%>%dplyr::filter(model=="RW")%>%
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val)%>%
  dplyr::group_by(param_name)%>%
  cor_test(sim,rec)%>%
  dplyr::mutate(model="RW")

param_corr_val_rws<-param_recov_long%>%dplyr::filter(model=="RWS")%>%
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val)%>%
  dplyr::group_by(param_name)%>%
  cor_test(sim,rec)%>%
  dplyr::mutate(model="RWS")

param_corr_val_wsls<-param_recov_long%>%dplyr::filter(model=="WSLS")%>%
           pivot_wider(id_cols=c(iter,model,param_name),names_from = param_status,values_from = val)%>%
  dplyr::group_by(param_name)%>%
  cor_test(sim,rec)%>%
  dplyr::mutate(model="WSLS")


param_rec_corr_vals<-bind_rows(param_corr_val_rw,param_corr_val_rws)%>%
  bind_rows(.,param_corr_val_wsls)

knitr::kable(param_rec_corr_vals,digits=2,caption="paramater recovery correlation values")

```



